---
title: "DO intervals"
author: "Abby Lewis"
date: "8/28/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(rLakeAnalyzer)
```

```{r}
# Load in CTD data
ctd <- read.csv("../../DO_modeling_data/CTD_final_2013_2020.csv")

# Load in bathymetry data
vol <- read_csv("../../DO_modeling_data/FCR Bathymetry.csv")
colnames(vol) <- c("Depth_m","Volume_L","SA_m2")

# Create a dataframe of oxygenation interval dates
turnover <- read_csv("../../DO_modeling_data/TurnoverDates_22Oct18.csv")
turnover <- turnover %>%
  mutate(Date_turnover = as.Date(turnover$Date, format = "%m/%d/%y"))%>%
  dplyr::select(-Date)
intGuide <- read_csv("../../DO_modeling_data/Hox_schedule_ungrouped.csv") %>%
  mutate(Year=year(Start),
         Start = as.Date(Start),
         End = as.Date(End)) %>%
  left_join(turnover %>% dplyr::select(-For2018,-Time)) %>%
  filter(Start<Date_turnover)
intGuide$End[is.na(intGuide$End)] <- intGuide$Date_turnover[is.na(intGuide$End)]
intGuide$End[intGuide$End>intGuide$Date_turnover] <- intGuide$Date_turnover[intGuide$End>intGuide$Date_turnover]
intGuide$Days = as.numeric(difftime(intGuide$End, intGuide$Start), units = "days")
```

Creating a dataset that is all of the CTD data but only at depths from bathymetry
```{r}
dt1 <- ctd
dt1$Date <- as.POSIXct(dt1$Date)
dt1_culled <- dt1 %>%
  filter(Site == 50 & Reservoir == "FCR" & !is.na(DO_mgL))

depths <- vol$Depth_m
# (Depths Can be changed as necessary)
df.final2<-dt1_culled %>% group_by(Date) %>% slice(which.min(abs(as.numeric(Depth_m) - depths[1]))) #Create a new dataframe
df.final2$Depth_m <- depths[1]
for (j in 2:length(depths)){ #loop through all depths and add the closest values to the final dataframe
  ctd_atThisDepth <- dt1_culled %>% group_by(Date) %>% slice(which.min(abs(as.numeric(Depth_m) - depths[j])))
  ctd_atThisDepth$Depth_m <- depths[j]
  df.final2 <- rbind(df.final2,ctd_atThisDepth)
}

thermo <- df.final2 %>%
  arrange(Date) %>%
  summarize(meta_bottom = meta.depths(Temp_C, Depth_m)[2])
mean(thermo$meta_bottom, na.rm = T) #5.31
thermo$meta_bottom<- 6 #Using constant thermocline depth
```

Creating a dataframe based upon the CTD data that calculates the volume-weighted hypolimnetic DO concentrations
```{r}
vw <- df.final2 %>%
  filter(as.Date(Date)!=as.Date("2017-07-06")) %>% ### WHy?????
  group_by(Date) %>%
  left_join(thermo, by = "Date") %>%
  mutate(Thermocline = meta_bottom) %>% 
  ungroup() %>%
  left_join(vol, by = "Depth_m")%>%
  mutate(DO_Weighted = DO_mgL*Volume_L,
         TP_Weighted = Temp_C*Volume_L) %>%
  filter(Depth_m >= Thermocline,) %>%
  group_by(Date) %>%
  summarize(
    thermo_depth = unique(Thermocline),
    Vol_Weighted_DO = sum(DO_Weighted),
    hypoVolume = sum(Volume_L),
    Conc = Vol_Weighted_DO/hypoVolume,
    Temp = sum(TP_Weighted)/hypoVolume,
    Temp_sed = last(Temp_C),
    Chla_ugL = mean(Chla_ugL),
    SA_m2 = mean(SA_m2))
write.csv(vw, "../../DO_modeling_data/vol_weighted_do_fcr_28Aug.csv")
```


This is necessary REGARDLESS of whether you are doing weekly or whole-interval
```{r}
vw2 <- vw

#Creates the dataframe with background information for each interval (start, end, SSS, etc)

vw2$ClosestStart <- NA
vw2$DaysSinceStart <- NA
vw2$Date <- as.Date(vw2$Date)
vw2$SSS <- NA
vw2$scfm <- NA
vw2$IntervalStart <- as.Date(NA)
vw2$IntervalEnd <- as.Date(NA)
for(i in seq(1:nrow(vw2))){
  distance <- as.numeric(difftime(vw2$Date[i], intGuide$Start, units = "days"))
  distance[distance<0] <- NA
  if(all(is.na(distance))){
    vw2$ClosestStart[i] <- 0
  } else {
      vw2$ClosestStart[i] <- which.min(distance)
      vw2$IntervalStart[i] <- intGuide$Start[which.min(distance)]
      vw2$IntervalEnd[i] <- intGuide$End[which.min(distance)]
      vw2$DaysSinceStart[i] <- min(distance, na.rm = TRUE)
      vw2$SSS[i] <- as.character(intGuide$SSS[which.min(distance)])
      vw2$scfm[i] <- intGuide$scfm[which.min(distance)]
      distanceEnd <- as.numeric(difftime(vw2$Date[i], intGuide$End, units = "days"))
      distanceEnd[distanceEnd<=0] <- NA
      if(min(distance, na.rm = TRUE) > min(distanceEnd, na.rm = TRUE)) { #Getting rid of points after the end of the season
            vw2$ClosestStart[i] <- NA
            vw2$DaysSinceStart[i] <- NA
            vw2$SSS[i] <- NA
            vw2$scfm[i] <- NA
            vw2$IntervalStart[i] <- NA
            vw2$IntervalEnd[i] <- NA
    }
  }
}

#Creates an additional dataframe to join with vw2. 
#fixEndpoints has only the end dates and it adds them at the END of the correct interval, since they will otherwise be processed only as the beginning point of the next one

fixEndpoints <- vw2 %>%
  filter(DaysSinceStart == 0)
for(i in seq(1:nrow(fixEndpoints))){
  distance <- as.numeric(difftime(fixEndpoints$Date[i], intGuide$Start, units = "days"))
  distance[distance<0] <- NA
  distance[distance == fixEndpoints$DaysSinceStart[i]] <- NA
  if(all(is.na(distance))){
    fixEndpoints$ClosestStart[i] <- 0
  } else {
      fixEndpoints$ClosestStart[i] <- which.min(distance)
      fixEndpoints$IntervalStart[i] <- intGuide$Start[which.min(distance)]
      fixEndpoints$IntervalEnd[i] <- intGuide$End[which.min(distance)]
      fixEndpoints$DaysSinceStart[i] <- min(distance, na.rm = TRUE)
      fixEndpoints$SSS[i] <- as.character(intGuide$SSS[which.min(distance)])
      fixEndpoints$scfm[i] <- intGuide$scfm[which.min(distance)]
      distanceEnd <- as.numeric(difftime(fixEndpoints$Date[i], intGuide$End, units = "days"))
      distanceEnd[distanceEnd<=0] <- NA
      if(min(distance, na.rm = TRUE) > min(distanceEnd, na.rm = TRUE)) {
            fixEndpoints$ClosestStart[i] <- NA
            fixEndpoints$DaysSinceStart[i] <- NA
            fixEndpoints$SSS[i] <- NA
            fixEndpoints$scfm[i] <- NA
            fixEndpoints$IntervalStart[i] <- NA
            fixEndpoints$IntervalEnd[i] <- NA
    }
  }
}
vw2 = vw2 %>%
  full_join(fixEndpoints)%>%
  mutate(Year = year(Date))%>%
  left_join(turnover, by = "Year") %>%
  filter(Date<Date_turnover) %>%
  dplyr::select(-Time,-For2018,-Year)
```

Adding supplimental data
```{r}
#Loading GHG data
ghgs<- read.csv("../../DO_modeling_data/Dissolved_CO2_CH4_Virginia_Reservoirs.csv")
fcr_ghgs = ghgs%>%filter(Reservoir == "FCR", 
              Site == 50)%>%
  mutate(Date = as.Date(DateTime))

# Bathymetry
vol <- read_csv("../../DO_modeling_data/FCR Bathymetry.csv")
colnames(vol) <- c("Depth_m","Volume_L","SA_m2")

#Iron
metals <- read.csv("../../DO_modeling_data/metals_EDI_current.csv")%>%
  filter(Reservoir == "FCR",
         Site == 50)%>%
  mutate(Date = as.Date(DateTime, format = "%m/%d/%Y %H:%M:%S"))

#DOC
chemistry <- read.csv("../../DO_modeling_data/chemistry.csv")%>%
  filter(Reservoir == "FCR",
         Site == 50)%>%
  mutate(Date = as.Date(DateTime))

ghg_depths <- c(0.1, 1.6, 3.8, 5, 6.2, 8, 9)
lower = 0
upper = ghg_depths[1]+(ghg_depths[2]-ghg_depths[1])/2
ghg_vols = c(sum(vol$Volume_L[vol$Depth_m < upper & vol$Depth_m > lower]))
ghg_layer_depth <- c()
ghg_layer_depth[1] <- upper-lower
for (d in 2:length(ghg_depths)){
  lower = ghg_depths[d]-(ghg_depths[d]-ghg_depths[d-1])/2
  upper = ghg_depths[d]+(ghg_depths[d+1]-ghg_depths[d])/2
  if(d == length(ghg_depths-1)){upper = 9.3}
  ghg_vols = c(ghg_vols, sum(vol$Volume_L[vol$Depth_m < upper & vol$Depth_m > lower]))
  ghg_layer_depth[d] <- upper-lower
}
vol2 = data.frame(ghg_depths,ghg_vols, ghg_layer_depth)

fcr_fe_formatted = metals %>%
  mutate(Depth_m = as.numeric(Depth_m)) %>%
  full_join(vol2, by = c("Depth_m"="ghg_depths")) %>%
  filter(Reservoir == "FCR", Depth_m %in% c(0.1, 1.6, 3.8, 5, 6.2, 8, 9)) %>%
  group_by(Date, Depth_m)%>%
  summarise(TFe_mgL_sd = sd(TFe_mgL),
            TFe_mgL = mean(TFe_mgL, na.rm = T),
            layer_vol = unique(ghg_vols),
            layer_depth = unique(ghg_layer_depth)) %>%
  filter(Depth_m>6)%>%
  group_by(Date)%>%
  mutate(n = length(unique(Depth_m)))%>%
  filter(n == 3)%>%
  mutate(fe_in_layer = TFe_mgL)%>%
  summarize(TFe_mgL = sum(fe_in_layer))

fcr_doc_formatted = chemistry %>%
  mutate(Depth_m = as.numeric(Depth_m)) %>%
  full_join(vol2, by = c("Depth_m"="ghg_depths")) %>%
  filter(Reservoir == "FCR", Depth_m %in% c(0.1, 1.6, 3.8, 5, 6.2, 8, 9)) %>%
  group_by(Date, Depth_m)%>%
  summarise(DOC_mgL = mean(DOC_mgL, na.rm = T),
            layer_vol = unique(ghg_vols),
            layer_depth = unique(ghg_layer_depth)) %>%
  filter(Depth_m>6)%>%
  group_by(Date)%>%
  mutate(n = length(unique(Depth_m)))%>%
  filter(n == 3)%>%
  mutate(doc_in_layer = DOC_mgL)%>%
  summarize(DOC_mgL = sum(doc_in_layer))%>%
  filter(!is.na(DOC_mgL))

fcr_ghg_formatted = fcr_ghgs %>%
  mutate(Depth_m = as.numeric(Depth_m)) %>%
  full_join(vol2, by = c("Depth_m"="ghg_depths")) %>%
  filter(Reservoir == "FCR", Depth_m %in% c(0.1, 1.6, 3.8, 5, 6.2, 8, 9)) %>%
  group_by(Date, Depth_m)%>%
  summarise(ch4_sd = sd(ch4_umolL),
            co2_sd = sd(co2_umolL),
            ch4_umolL = mean(ch4_umolL, na.rm = T),
            co2_umolL = mean(co2_umolL, na.rm = T),
            layer_vol = unique(ghg_vols),
            layer_depth = unique(ghg_layer_depth)) %>%
  filter(Depth_m>6)%>%
  group_by(Date)%>%
  mutate(n = length(unique(Depth_m)))%>%
  filter(n == 3)%>%
  mutate(co2_in_layer = co2_umolL,
         ch4_in_layer = ch4_umolL)%>%
  summarize(co2_vw_umolL = sum(co2_in_layer),
            ch4_vw_umolL = sum(ch4_in_layer))

fcr_fe_formatted%>%
  ggplot(aes(x = Date, y = TFe_mgL))+
  geom_point()

fcr_doc_formatted%>%
  ggplot(aes(x = Date, y = DOC_mgL))+
  geom_point()

vw2 = vw2%>%
  full_join(fcr_fe_formatted)%>%
  full_join(fcr_doc_formatted)%>%
  full_join(fcr_ghg_formatted)


```



This is ONLY for weekly (two week intervals)
```{r}
vw2_week <- vw2
#This section sets it up to divide into weeks
vw2_week$WeeksSinceStart <- floor(vw2_week$DaysSinceStart/14)
repStartEnd <- vw2_week %>%
  filter(DaysSinceStart !=0, 
         DaysSinceStart %% 14 == 0)%>%
  mutate(WeeksSinceStart = WeeksSinceStart - 1) #Duplicate endpoints
vw2_week = vw2_week %>%
  full_join(repStartEnd)

slope_temp_wk <- vw2_week %>%
  filter(ClosestStart>0)%>%
  group_by(ClosestStart, WeeksSinceStart) %>%
  summarize(
    temp = mean(Temp),
    Date_start = min(Date),
    Date_end = max(Date),
    IntStart = unique(IntervalStart),
    IntEnd = unique(IntervalEnd),
    Observations = n(),
    mg_L_day_O2 = mean(scfm)*50*1000000/mean(hypoVolume),
    SSS = unique(SSS),
    temp_sed = mean(Temp),
    temp_init = first(Temp),
    temp_final = last(Temp),
    doc_init = first(DOC_mgL),
    doc_mean = mean(DOC_mgL, na.rm = T),
    Fe_init = first(TFe_mgL),
    Fe_mean = mean(TFe_mgL, na.rm = T),
    o2_init = first(Conc),
    o2_mean = mean(Conc),
    dist_turnover =as.numeric(difftime(unique(Date_turnover),IntStart, units = "days")),
    thermo_start = first(thermo_depth),
    thermo_end = last(thermo_depth),
    thermo_mean = mean(thermo_depth)
    )

slopes_wk_do <- vw2_week%>%
  filter(ClosestStart>0)%>%
  group_by(ClosestStart, WeeksSinceStart) %>%
  do(intercept_do = as.numeric(lm(Conc~ Date, data = .)$coefficients[1]),
     slope_do = as.numeric(lm(Conc~ Date, data = .)$coefficients[2]))

slopes_wk_co2 <- vw2_week%>%
  filter(ClosestStart>0)%>%
  group_by(ClosestStart, WeeksSinceStart) %>%
  filter(sum(!is.na(co2_vw_umolL))>0)%>%
  do(intercept_co2 = as.numeric(lm(co2_vw_umolL~ Date, data = .)$coefficients[1]),
     slope_co2 = as.numeric(lm(co2_vw_umolL~ Date, data = .)$coefficients[2]))

slope_temp_wk = slope_temp_wk %>%
  left_join(slopes_wk_do, by = c("ClosestStart", "WeeksSinceStart")) %>%
  filter(Date_start != IntEnd) %>%
  mutate(slope_do = unlist(slope_do),
         intercept_do = unlist(intercept_do),
         slope_O2 = slope_do - mg_L_day_O2)%>%
  left_join(slopes_wk_co2%>%
              mutate(slope_co2 = unlist(slope_co2),
                     intercept_co2 = unlist(intercept_co2)), by = c("ClosestStart", "WeeksSinceStart") )
slope_temp_wk_2obs <- slope_temp_wk %>%
  filter(Observations >=2)
write.csv(slope_temp_wk_2obs, "slope_temp_wk_2obs.csv", row.names = F)
```

Months
```{r}
vw2_week <- vw2
#This section sets it up to divide into weeks
vw2_week$WeeksSinceStart <- floor(vw2_week$DaysSinceStart/30)
repStartEnd <- vw2_week %>%
  filter(DaysSinceStart !=0, 
         DaysSinceStart %% 30 == 0)%>%
  mutate(WeeksSinceStart = WeeksSinceStart - 1) #Duplicate endpoints
vw2_week = vw2_week %>%
  full_join(repStartEnd)

slope_temp_wk <- vw2_week %>%
  filter(ClosestStart>0)%>%
  group_by(ClosestStart, WeeksSinceStart) %>%
  summarize(
    temp = mean(Temp),
    Date_start = min(Date),
    Date_end = max(Date),
    IntStart = unique(IntervalStart),
    IntEnd = unique(IntervalEnd),
    Observations = n(),
    mg_L_day_O2 = mean(scfm)*50*1000000/mean(hypoVolume),
    SSS = unique(SSS),
    temp_sed = mean(Temp),
    temp_init = first(Temp),
    temp_final = last(Temp),
    doc_init = first(DOC_mgL),
    doc_mean = mean(DOC_mgL, na.rm = T),
    Fe_init = first(TFe_mgL),
    Fe_mean = mean(TFe_mgL, na.rm = T),
    o2_init = first(Conc),
    o2_mean = mean(Conc),
    dist_turnover =as.numeric(difftime(unique(Date_turnover),IntStart, units = "days")),
    thermo_start = first(thermo_depth),
    thermo_end = last(thermo_depth),
    thermo_mean = mean(thermo_depth)
    )

slopes_wk_do <- vw2_week%>%
  filter(ClosestStart>0)%>%
  group_by(ClosestStart, WeeksSinceStart) %>%
  do(intercept_do = as.numeric(lm(Conc~ Date, data = .)$coefficients[1]),
     slope_do = as.numeric(lm(Conc~ Date, data = .)$coefficients[2]))

slopes_wk_co2 <- vw2_week%>%
  filter(ClosestStart>0)%>%
  group_by(ClosestStart, WeeksSinceStart) %>%
  filter(sum(!is.na(co2_vw_umolL))>0)%>%
  do(intercept_co2 = as.numeric(lm(co2_vw_umolL~ Date, data = .)$coefficients[1]),
     slope_co2 = as.numeric(lm(co2_vw_umolL~ Date, data = .)$coefficients[2]))

slope_temp_wk = slope_temp_wk %>%
  left_join(slopes_wk_do, by = c("ClosestStart", "WeeksSinceStart")) %>%
  filter(Date_start != IntEnd) %>%
  mutate(slope_do = unlist(slope_do),
         intercept_do = unlist(intercept_do),
         slope_O2 = slope_do - mg_L_day_O2)%>%
  left_join(slopes_wk_co2%>%
              mutate(slope_co2 = unlist(slope_co2),
                     intercept_co2 = unlist(intercept_co2)), by = c("ClosestStart", "WeeksSinceStart") )
slope_temp_month_3obs <- slope_temp_wk %>%
  filter(Observations >=3)
write.csv(slope_temp_month_3obs, "slope_temp_month_3obs.csv", row.names = F)
```



```{r}
#This does the same thing, but for intervals
vw2_int <- vw2

slope_temp_int <- vw2_int %>%
  filter(ClosestStart>0)%>%
  group_by(ClosestStart) %>%
  summarize(
    temp = mean(Temp),
    Date_start = min(Date),
    Date_end = max(Date),
    IntStart = unique(IntervalStart),
    IntEnd = unique(IntervalEnd),
    Observations = n(),
    mg_L_day_O2 = mean(scfm)*50*1000000/mean(hypoVolume),
    SSS = unique(SSS),
    temp_sed = mean(Temp),
    temp_init = first(Temp),
    temp_final = last(Temp),
    doc_init = first(DOC_mgL),
    doc_mean = mean(DOC_mgL, na.rm = T),
    Fe_init = first(TFe_mgL),
    Fe_mean = mean(TFe_mgL, na.rm = T),
    o2_init = first(Conc),
    o2_mean = mean(Conc),
    dist_turnover =as.numeric(difftime(unique(Date_turnover),IntStart, units = "days")),
    thermo_start = first(thermo_depth),
    thermo_end = last(thermo_depth),
    thermo_mean = mean(thermo_depth))

slopes_int_do <- vw2_int%>%
  filter(ClosestStart>0)%>%
  group_by(ClosestStart) %>%
  do(intercept_do = as.numeric(lm(Conc~ Date, data = .)$coefficients[1]),
     slope_do = as.numeric(lm(Conc~ Date, data = .)$coefficients[2]))

slopes_int_co2 <- vw2_int%>%
  filter(ClosestStart>0)%>%
  group_by(ClosestStart) %>%
  filter(sum(!is.na(co2_vw_umolL))>0)%>%
  do(intercept_co2 = as.numeric(lm(co2_vw_umolL~ Date, data = .)$coefficients[1]),
     slope_co2 = as.numeric(lm(co2_vw_umolL~ Date, data = .)$coefficients[2]))

slope_temp_int = slope_temp_int %>%
  left_join(slopes_int_do, by = c("ClosestStart")) %>%
  filter(Date_start != IntEnd) %>%
  mutate(slope_do = unlist(slope_do),
         intercept_do = unlist(intercept_do),
         slope_O2 = slope_do - mg_L_day_O2)%>%
  left_join(slopes_int_co2%>%
              mutate(slope_co2 = unlist(slope_co2),
                     intercept_co2 = unlist(intercept_co2)), by = c("ClosestStart") )
slope_temp_int_3obs <- slope_temp_int %>%
  filter(Observations >=3)
write.csv(slope_temp_int_3obs, "slope_temp_int_3obs.csv", row.names = F)
```


Plots of DO


```{r}
lim_bot <- min(-slope_temp_wk_2obs$slope_O2)
lim_top <- max(-slope_temp_wk_2obs$slope_O2)

jet.colors <- colorRampPalette(c("#00007F", "blue", "#007FFF", "cyan", "#7FFF7F", "yellow", "#FF7F00", "red", "#7F0000"))

g0 <- vw2_week%>%
  filter(ClosestStart>0) 

slopes_for_plot <- slope_temp_wk_2obs %>%
  filter(!is.na(slope_do)) %>%
  mutate(y0 = slope_do*as.numeric(Date_start)+intercept_do,
         y1 = slope_do*as.numeric(Date_end)+intercept_do,
         y1_o2 = y0 + slope_O2*as.numeric(Date_end-Date_start),
         Year = year(Date_start))

g0 %>%
  mutate(Year = year(Date))%>%
  ggplot(aes(x = as_datetime(Date),y = Conc))+
  geom_segment(aes(x = as_datetime(Date_start), 
                 y = y0, 
                 xend = as_datetime(Date_end), 
                 yend = y1, color = -slope_O2), data = slopes_for_plot,
             lwd = 3)+
  scale_color_gradientn(colours=jet.colors(7), limits = c(lim_bot,lim_top),na.value = "white")+
  geom_point(size = 2, pch = 1, alpha = 0.5)+
  #geom_vline(xintercept = on)+
  #geom_vline(xintercept = off,lty=2)+
  facet_grid(cols = vars(Year), scales = "free_x",space = "free_x")+
  ylab("Average hypolimnetic DO (mg/L)")+
  xlab("")+
  theme_bw()+
  theme(axis.text.x=element_blank(),
        axis.ticks = element_blank(),
        text = element_text(size = 13))
```


```{r}
lim_bot <- min(-slope_temp_month_3obs$slope_O2)
lim_top <- max(-slope_temp_month_3obs$slope_O2)

jet.colors <- colorRampPalette(c("#00007F", "blue", "#007FFF", "cyan", "#7FFF7F", "yellow", "#FF7F00", "red", "#7F0000"))

g0 <- vw2_week%>%
  filter(ClosestStart>0) 

slopes_for_plot <- slope_temp_month_3obs %>%
  filter(!is.na(slope_do)) %>%
  mutate(y0 = slope_do*as.numeric(Date_start)+intercept_do,
         y1 = slope_do*as.numeric(Date_end)+intercept_do,
         y1_o2 = y0 + slope_O2*as.numeric(Date_end-Date_start),
         Year = year(Date_start))

p = g0 %>%
  mutate(Year = year(Date))%>%
  ggplot(aes(x = as_datetime(Date),y = Conc))+
  geom_segment(aes(x = as_datetime(Date_start), 
                 y = y0, 
                 xend = as_datetime(Date_end), 
                 yend = y1, color = -slope_O2), data = slopes_for_plot,
             lwd = 3)+
  scale_color_gradientn(colours=jet.colors(7), limits = c(lim_bot,lim_top),na.value = "white")+
  geom_point(size = 2, pch = 1, alpha = 0.5)+
  #geom_vline(xintercept = on)+
  #geom_vline(xintercept = off,lty=2)+
  facet_grid(cols = vars(Year), scales = "free_x",space = "free_x")+
  ylab("Average hypolimnetic DO (mg/L)")+
  xlab("")+
  theme_bw()+
  theme(axis.text.x=element_blank(),
        axis.ticks = element_blank(),
        text = element_text(size = 13))

p

jpeg("o2_month_intervals.jpg",width = 6, height = 4, units = "in", res = 300)
p
dev.off()
```


```{r}
lim_bot <- min(-slope_temp_int_3obs$slope_O2)
lim_top <- max(-slope_temp_int_3obs$slope_O2)

jet.colors <- colorRampPalette(c("#00007F", "blue", "#007FFF", "cyan", "#7FFF7F", "yellow", "#FF7F00", "red", "#7F0000"))

g0 <- vw2_week%>%
  filter(ClosestStart>0) 

slopes_for_plot <- slope_temp_int_3obs %>%
  filter(!is.na(slope_do)) %>%
  mutate(y0 = slope_do*as.numeric(Date_start)+intercept_do,
         y1 = slope_do*as.numeric(Date_end)+intercept_do,
         y1_o2 = y0 + slope_O2*as.numeric(Date_end-Date_start),
         Year = year(Date_start))

g0 %>%
  mutate(Year = year(Date))%>%
  ggplot(aes(x = as_datetime(Date),y = Conc))+
  geom_segment(aes(x = as_datetime(Date_start), 
                 y = y0, 
                 xend = as_datetime(Date_end), 
                 yend = y1, color = -slope_O2), data = slopes_for_plot,
             lwd = 3)+
  scale_color_gradientn(colours=jet.colors(7), limits = c(lim_bot,lim_top),na.value = "white")+
  geom_point(size = 2, pch = 1, alpha = 0.5)+
  #geom_vline(xintercept = on)+
  #geom_vline(xintercept = off,lty=2)+
  facet_grid(cols = vars(Year), scales = "free_x",space = "free_x")+
  ylab("Average hypolimnetic DO (mg/L)")+
  xlab("")+
  theme_bw()+
  theme(axis.text.x=element_blank(),
        axis.ticks = element_blank(),
        text = element_text(size = 13))
```


Plots of CO2



```{r}
g0 <- vw2_week%>%
  filter(ClosestStart>0) 

slopes_for_plot <- slope_temp_int_3obs %>%
  filter(!is.na(slope_co2)) %>%
  mutate(y0 = slope_co2*as.numeric(Date_start)+intercept_co2,
         y1 = slope_co2*as.numeric(Date_end)+intercept_co2,
         Year = year(Date_start))
lim_bot <- min(slope_temp_int_3obs$slope_co2)
lim_top <- max(slope_temp_int_3obs$slope_co2)

jet.colors <- colorRampPalette(c("#00007F", "blue", "#007FFF", "cyan", "#7FFF7F", "yellow", "#FF7F00", "red", "#7F0000"))

g0 %>%
  mutate(Year = year(Date))%>%
  ggplot(aes(x = as_datetime(Date),y = co2_vw_umolL))+
  geom_segment(aes(x = as_datetime(Date_start), 
                 y = y0, 
                 xend = as_datetime(Date_end), 
                 yend = y1, color = -slope_co2), data = slopes_for_plot,
             lwd = 3)+
  scale_color_gradientn(colours=jet.colors(7), limits = c(lim_bot,lim_top),na.value = "white")+
  geom_point(size = 2, pch = 1, alpha = 0.5)+
  facet_grid(cols = vars(Year), scales = "free_x",space = "free_x")+
  ylab("Average hypolimnetic CO2 (umol/L)")+
  xlab("")+
  theme_bw()+
  theme(axis.text.x=element_blank(),
        axis.ticks = element_blank(),
        text = element_text(size = 13))
```

```{r}
g0 <- vw2_week%>%
  filter(ClosestStart>0) 

slopes_for_plot <- slope_temp_wk_2obs %>%
  filter(!is.na(slope_co2)) %>%
  mutate(y0 = slope_co2*as.numeric(Date_start)+intercept_co2,
         y1 = slope_co2*as.numeric(Date_end)+intercept_co2,
         Year = year(Date_start))
lim_bot <- min(-slope_temp_wk_2obs$slope_co2)
lim_top <- max(-slope_temp_wk_2obs$slope_co2)

jet.colors <- colorRampPalette(c("#00007F", "blue", "#007FFF", "cyan", "#7FFF7F", "yellow", "#FF7F00", "red", "#7F0000"))

g0 %>%
  mutate(Year = year(Date))%>%
  ggplot(aes(x = as_datetime(Date),y = co2_vw_umolL))+
  geom_segment(aes(x = as_datetime(Date_start), 
                 y = y0, 
                 xend = as_datetime(Date_end), 
                 yend = y1, color = -slope_co2), data = slopes_for_plot,
             lwd = 3)+
  scale_color_gradientn(colours=jet.colors(7), limits = c(lim_bot,lim_top),na.value = "white")+
  geom_point(size = 2, pch = 1, alpha = 0.5)+
  facet_grid(cols = vars(Year), scales = "free_x",space = "free_x")+
  ylab("Average hypolimnetic CO2 (umol/L)")+
  xlab("")+
  theme_bw()+
  theme(axis.text.x=element_blank(),
        axis.ticks = element_blank(),
        text = element_text(size = 13))
```


```{r}
g0 <- vw2_week%>%
  filter(ClosestStart>0) 

slopes_for_plot <- slope_temp_month_3obs %>%
  filter(!is.na(slope_co2)) %>%
  mutate(y0 = slope_co2*as.numeric(Date_start)+intercept_co2,
         y1 = slope_co2*as.numeric(Date_end)+intercept_co2,
         Year = year(Date_start))
lim_bot <- min(-slope_temp_month_3obs$slope_co2)
lim_top <- max(-slope_temp_month_3obs$slope_co2)

jet.colors <- colorRampPalette(c("#00007F", "blue", "#007FFF", "cyan", "#7FFF7F", "yellow", "#FF7F00", "red", "#7F0000"))

p = g0 %>%
  mutate(Year = year(Date))%>%
  ggplot(aes(x = as_datetime(Date),y = co2_vw_umolL))+
  geom_segment(aes(x = as_datetime(Date_start), 
                 y = y0, 
                 xend = as_datetime(Date_end), 
                 yend = y1, color = -slope_co2), data = slopes_for_plot,
             lwd = 3)+
  scale_color_gradientn(colours=jet.colors(7), limits = c(lim_bot,lim_top),na.value = "white")+
  geom_point(size = 2, pch = 1, alpha = 0.5)+
  facet_grid(cols = vars(Year), scales = "free_x",space = "free_x")+
  ylab("Average hypolimnetic CO2 (umol/L)")+
  xlab("")+
  theme_bw()+
  theme(
        axis.ticks = element_blank(),
        text = element_text(size = 13))

jpeg("co2_month_intervals.jpg",width = 6, height = 4, units = "in", res = 300)
p
dev.off()
```
