---
title: "DO Model Hindcasting"
author: "Abby Lewis"
date: "12/8/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readxl)
library(tidyverse)
library(zoo)
library(deSolve)
library(lubridate)
library(formatR)
library(knitr)
source('EnKF_functions_21Mar20.R')
library(magick)
library(animation)
library(Metrics)
```

Created 20 March 20 to convert my model to a forecasting framework
- NOTE: got rid of the flexible hypo volume. I think that's what was destroying 2016
- NOTE: I am saying data collected on the day of the forecast DOES get incorporated into the forecast

To do:
- ***Start comparing different models***
  - Just temp
  - Just oxygen
  - Just SSS
- READ about forecast evaluation
- Look into best practices for archiving forecast runs. Do I need to save all drivers/parameters/etc from each run?

Should the model only run when you have a new observation?
  - Yes. Drivers aren't changing. There's no point in rerunning the forecast, and this will lead to more noise in the RMSE plot
  - Okay but it does pretty well and managers could potentially use it to predict further into the future even with out a new observation
  - Not a huge priority. Look into best practices for how often the model should be run. Sticking with an even time step for now for simplicity. 

Done:
- Set aside some data as test (2013, 2015, 2019) and some as training (2014, 2016, 2017, 2018): DONE
- Create one forecast half way through 2014: DONE
- Create forecasts for all of 2014: DONE
- Create forecasts for all training years: DONE
- Set this up to archive everything in github: DONE!!
- Calculate RMSE a certain number of days out DONE
- Plot of rmse vs the number of days away, colors for the year DONE
- Archive forecasts DONE
- Create persistence forecast DONE
- Compare RMSE with the persistence forecast to the actual model


## Model
```{r}

O2_model <- function(times, states, parms, inputs){
  
  #STATES 
  O2_mgL <- states[1]

  #PARMS 
  R20 <- as.numeric(parms[1])
  theta <- as.numeric(parms[2])
  ko2 <- as.numeric(parms[3])
  sss_scalar <- as.numeric(parms[4])
  
  #INPUT
  SSS <- inputs[1]
  temp <- inputs[2]
  
  #CALCULATIONS
  R = R20*theta^(temp-20)*O2_mgL/(O2_mgL+ko2)
  scalar = 1
  if(SSS>0){
    scalar = sss_scalar
  }
  OD = R*scalar

  #DERIVATIVE
  dO2_mgLdt <- SSS-OD

  #RETURN A LIST OF THE DERIVATIVES
  return(list(c(dO2_mgLdt), c(parms)))
}
```

## Parameters
```{r}
parms <- c(
  R20 = .7, #mg/L/day
  theta = 1.1, 
  ko2 = 1, #mg/L
  sss_scalar = 3
)
```

```{r} 
# From GLEON workshop 
# I made all of these up more or less randomly. Not sure how I should have come up with them


n_en = 100 # number of ensembles 
# coefficient of variation (CV) as a representation of uncertainty 
param_cv = c(R20 = .1,
             theta = .01,
             ko2 = .1,
             sss_scalar = .2)
driver_cv = c(SSS = .2,
    temp = .2) # Coefficient of variation of driver data 
init_cond_cv = .1
obs_cv = 0.05
```

```{r}
#Create observations dataframe
  CTD <- read.csv("../DO_modeling_data/vol_weighted_do_fcr.csv")
  CTD = CTD%>%
    filter(hypoVolume>0,
           !is.na(Conc))%>%
    mutate(Date = as.Date(Date))
  obs <- CTD %>%
    filter(!is.na(Conc))%>%
    select(Date, Conc)%>%
    rename(datetime = Date)%>%
    group_by(datetime)%>%
    summarize(O2_mgL = mean(Conc))
  CTD$hypoVolume<-mean(CTD$hypoVolume, na.rm = TRUE)
  
  mean_hypo_ratio <- mean(CTD$SA_m2/CTD$hypoVolume)
  median_hypo_ratio <- median(CTD$SA_m2/CTD$hypoVolume)
  
#Create driver data frame (called model_inputs)
  SSS <- read_excel("../DO_modeling_data/Calc_HOX_flow_DO_20190320.xlsx") 
  SSS$time <- as.Date(SSS$time)
```


```{r}
inputs_year<- function(start, stop){
  dates = data.frame(seq(start,stop,by = "days"))
  colnames(dates) <- "Date"
  inputs = dates %>%
    left_join(CTD %>%
                dplyr::select(Date,Conc,Temp,hypoVolume,thermo_depth,Chla_ugL,SA_m2), by = "Date")%>%
    left_join(SSS %>% 
                dplyr::select(time, scfm), by = c("Date"="time"))%>%
    arrange(Date)
  if(all(is.na(inputs$Chla_ugL))){
    inputs$Chla_ugL<-1
  }
  inputs = inputs%>%
    group_by(Date)%>%
    summarise(Conc = mean(Conc),
              Temp = mean(Temp),
              hypoVolume = mean(hypoVolume),
              thermo_depth = mean(thermo_depth),
              scfm = mean(scfm),
              Chla = mean(Chla_ugL),
              SA = mean(SA_m2))
}

run_do_hindcast <- function(inputs, obs, today, n_days = 14){
  obs = obs%>%
    filter(datetime<=today)
  inputs = inputs%>%
    filter(Date<=stop, 
           Date>=start,
           Date<=today+n_days)
  inputs[inputs$Date > today,c(2,3,4,5,7,8)] <- NA
  inputs = inputs%>%
    mutate(Conc = na.approx(Conc, rule = 2),
           Temp = na.approx(Temp, rule = 2),
           hypoVolume = na.approx(hypoVolume, rule = 2),
           thermo_depth = na.approx(thermo_depth, rule = 2),
           scfm = ifelse(Date>=as.Date("2013-05-15"),scfm,0),
           SSS_add_conc = scfm*50*1000000/hypoVolume,
           Chla = na.approx(Chla, rule = 2),
           SA = na.approx(SA, rule = 2))
  simulation_time <- as.numeric(difftime(min(today+n_days, stop), start, unit = "days")+1) #days
  #Assemble driver data
  model_inputs <- list(datetime = inputs$Date,
    SSS = inputs$SSS_add_conc,
    temp = inputs$Temp)
  model_inputs<- data.frame(model_inputs)
  
  #Set initial conditions
  yini <- c(
    O2_mgL = inputs$Conc[inputs$Date == start]
  )

  
  #Run EnKF
  est_out = EnKF(n_en = n_en, 
           start = start,
           stop = min(stop, today+n_days),
           time_step = "days",
           obs_file = obs, 
           driver_file = model_inputs, 
           n_states_est = 1,
           n_params_est = 4,
           n_params_obs = 0,
           n_drivers = 2,
           parm_init = parms, 
           obs_cv = obs_cv,
           param_cv = param_cv,
           driver_cv = driver_cv, 
           init_cond_cv = init_cond_cv)
  return(est_out)
}

plot_hindcast <- function(est_out){
  par(mfrow = c(2,3))
  param_names = c("R20","theta","ko2","sss_scalar","chla_vmax")
  plot_param = function(est_out,num,name = "Parameter value"){
    num = num+1
    mean_param_est = apply(est_out$Y[num,,], 1, FUN = mean)
    plot(mean_param_est ~ est_out$dates, type ='l', 
         ylim = range(est_out$Y[num,,]),
         col = 'grey', ylab = name, xlab ='', main = param_names[num-1])
    for(i in 2:n_en){
      lines(est_out$Y[num,,i] ~ est_out$dates, col = 'grey')
    }
    lines(mean_param_est ~ est_out$dates, col = 'black', lwd = 2)
  }
  for(i in seq(1,length(param_names))){
    plot_param(est_out,i)
  }
}


plot_o2 = function(est_out, today, start, stop, n_days = 14){
  mean_o2_est = apply(est_out$Y[1,,], 1, FUN = mean)
  plot(mean_o2_est ~ est_out$dates, type ='l', 
       ylim = c(-1,25),#max(c(est_out$Y[1,,], est_out$obs[1,,]),na.rm = T)),
       col = 'grey', ylab = 'O2 (mg L-1)', xlab = '',main = year(est_out$dates[1]), xlim = c(start, stop))
  for(i in 2:n_en){
    lines(est_out$Y[1,,i] ~ est_out$dates, 
          col = 'grey')
  }
  lines(mean_o2_est ~ est_out$dates, col = 'black', lwd =2 )
  future_obs <- obs[obs$datetime>today&obs$datetime<=(today+n_days),]
  obs <- obs[obs$datetime<=today,]
  points(obs$O2_mgL~obs$datetime, pch = 16, col = rgb(1,0,0))
  points(future_obs$O2_mgL~future_obs$datetime, pch = 16, col = rgb(0,0,1))
  abline(v = today)
  #arrows(est_out$dates, est_out$obs[1,,] - 
   #        est_out$state_sd, 
    #     est_out$dates, est_out$obs[1,,] +
     #      est_out$state_sd, 
      #   code = 3, length = 0.1, angle = 90, col = 'red')
}

plot_param = function(est_out,num,name = "Parameter value"){
  num = num+1
  mean_param_est = apply(est_out$Y[num,,], 1, FUN = mean)
  plot(mean_param_est ~ est_out$dates, type ='l', 
       ylim = range(est_out$Y[num,,]),
       col = 'grey', ylab = name, xlab ='', main = year(est_out$dates[1]))
  for(i in 2:n_en){
    lines(est_out$Y[num,,i] ~ est_out$dates, col = 'grey')
  }
  lines(mean_param_est ~ est_out$dates, col = 'black', lwd = 2)
}

createResultsDF <- function(start, stop){
  days <- as.numeric(difftime(stop,start, units = "days"))
  rows <- floor(days/run_space)+1
  cols <- n_days*2+1
  results <- matrix(NA, nrow = rows, ncol = cols)
  n <- rep(seq(1,n_days))
  type <- rep(c("_pred","_obs"),each = n_days)
  col_names <- c("TODAY",paste("PLUS",n,type,sep = ""))
  colnames(results)<-col_names
  return(results)
}

extendObsDF <- function(start,stop,obs){
  dates = data.frame(seq(start,stop,by = "days"))
  colnames(dates) <- "datetime"
  obs_allDates = dates %>%
    left_join(obs)
  return(obs_allDates)
}

createRmseDF <- function(n_days,results){
  n <- seq(1,n_days)
  val <- rep(NA,n_days)
  class(val) <- "numeric"
  rmse_thisYear <- data.frame(n,val)
  results <- as.data.frame(results)
  for(i in seq(1:n_days)){
    predicted <- results[i+1]
    observed <- results[i+1+n_days]
    rmse_thisYear$val[rmse_thisYear$n == i] <- rmse(observed[!is.na(observed)], predicted[!is.na(observed)])
  }
  rmse_thisYear
}

runForecasts <- function(start, stop, n_days, run_space, obs, gif = TRUE, archiveForecasts = FALSE, remove = FALSE, delay = 30){
  #Create results dataframe
  results<- createResultsDF(start, stop)
  #Create obs file with all dates (filling dates for NAs)
  obs_allDates <- extendObsDF(start,stop,obs)
  #Create inputs (drivers) for this year
  inputs_thisYear <- inputs_year(start,stop)
  today <- start
  if(gif == TRUE){
    dateRun <- format(Sys.Date(),"%d%b%y")
    year <- year(start)
    dir1 <- paste("../DO_modeling_figures",dateRun,sep = "/")
    dir2<-paste(dir1,year,sep = "/")
    dir.create(dir1)
    dir.create(dir2)
    #setwd(dir2)
    png(file=paste(dir2,"/forecast%03d.png",sep=""), width=480, height=480)
  }
  while(today < stop){
    row<- as.numeric(difftime(today,start))/run_space+1
    cols <- n_days*2+1
    est_thisYear <- run_do_hindcast(inputs_thisYear, obs, today, n_days)
    mean_o2_est <- apply(est_thisYear$Y[1,,], 1, FUN = mean)
    obs_toAdd <- obs_allDates$O2_mgL[obs_allDates$datetime>today & obs_allDates$datetime<=today+n_days]
    if(length(obs_toAdd)<n_days){
      obs_toAdd<-c(obs_toAdd, rep(NA,n_days-length(obs_toAdd)))
    }
    results[row,(2+n_days):cols]<- obs_toAdd
    results[row,2:(1+n_days)]<-tail(mean_o2_est, n = n_days)
    results[row,1]<-today
    if(gif == TRUE){
      plot_o2(est_thisYear, today, start, stop)
    }
    if(archiveForecasts == TRUE){
      dateRun <- format(Sys.Date(),"%d%b%y")
      year <- year(start)
      dir1.1 <- paste("../Archived_forecasts",dateRun,sep = "/")
      dir2.1<-paste(dir1.1,year,sep = "/")
      dir.create(dir1.1)
      dir.create(dir2.1)
      write.csv(est_thisYear$Y[1,,],paste(dir2,"/",format(today,"%d%b%y"),".csv",sep = ""))
    }
    today <- today+run_space
  }
  if (gif == TRUE){
    convert <- paste("convert -delay ",delay," ",dir2,"/forecast*.png ",dir2,"/animated_count_down.gif", sep = "")
    system(convert)
    dev.off()
    # Remove png files
    if(remove == TRUE){
      file.remove(list.files(pattern=".png"))
    }
  }
  return(results)
}


persistenceForecast <- function(start,stop,n_days,run_space,obs){
  #Create results dataframe
  results<- createResultsDF(start, stop)
  #Create obs file with all dates (filling dates for NAs)
  obs_allDates <- extendObsDF(start,stop,obs)
  today <- start
  while(today < stop){
    row<- as.numeric(difftime(today,start))/run_space+1
    cols <- n_days*2+1
    current_obs <- obs[obs$datetime<=today,]
    most_recent_obs <- current_obs$O2_mgL[which.max(current_obs$datetime)]
    forecast <- rep(most_recent_obs,n_days)
    obs_toAdd <- obs_allDates$O2_mgL[obs_allDates$datetime>today & obs_allDates$datetime<=today+n_days]
    if(length(obs_toAdd)<n_days){
      obs_toAdd<-c(obs_toAdd, rep(NA,n_days-length(obs_toAdd)))
    }
    results[row,(2+n_days):cols]<- obs_toAdd
    results[row,2:(1+n_days)]<-forecast
    results[row,1]<-today
    today <- today+run_space
  }
  results 
}
```







Run forecasts!
```{r}
run_space <- 1 #Number of days between runs of the model
n_days <- 14 #Forecast horizon

#2014
start = as.Date("2014-06-02")
stop = as.Date("2014-10-15")
results_2014 <- runForecasts(start, stop, n_days, run_space, obs, delay = 5)
rmse_2014 <- createRmseDF(n_days, results_2014) # Calculate rmse for all days

#2016
start = as.Date("2016-06-01")
stop = as.Date("2016-10-07")
results_2016 <- runForecasts(start, stop, n_days, run_space, obs, delay = 5)
rmse_2016 <- createRmseDF(n_days, results_2016)

#2017
start = as.Date("2017-06-28")
stop = as.Date("2017-07-12")
results_2017 <- runForecasts(start, stop, n_days, run_space, obs, delay = 30)
rmse_2017 <- createRmseDF(n_days, results_2017)

#2018
start = as.Date("2018-06-04")
stop = as.Date("2018-10-22")
results_2018 <- runForecasts(start, stop, n_days, run_space, obs, delay = 5)
rmse_2018 <- createRmseDF(n_days, results_2018)

rmse_total <- rmse_2014%>%
  mutate(Year = 2014)%>%
  full_join(rmse_2016 %>% mutate (Year = 2016))%>%
  full_join(rmse_2017 %>% mutate (Year = 2017))%>%
  full_join(rmse_2018 %>% mutate (Year = 2018))
write.csv(rmse_total,"../DO_modeling_results/rmse_23Mar20.csv")

rmse_total%>%
  filter(Year!=2017)%>%
  ggplot(aes(x = n, y = val, col = as.factor(Year)))+
  geom_point()+
  ylab("RMSE")+
  xlab("Days past forecast generation")+
  labs(color = "Year")
```


```{r}
run_space <- 1 #Number of days between runs of the model
n_days <- 14 #Forecast horizon

#2014
start = as.Date("2014-06-02")
stop = as.Date("2014-10-15")
persist_2014 <- persistenceForecast(start, stop, n_days, run_space, obs)
rmse_persist_2014 <- createRmseDF(n_days, persist_2014)

#2016
start = as.Date("2016-06-01")
stop = as.Date("2016-10-07")
persist_2016 <- persistenceForecast(start, stop, n_days, run_space, obs)
rmse_persist_2016 <- createRmseDF(n_days, persist_2016)

#2017
start = as.Date("2017-06-28")
stop = as.Date("2017-07-12")
persist_2017 <- persistenceForecast(start, stop, n_days, run_space, obs)
rmse_persist_2017 <- createRmseDF(n_days, persist_2017)

#2018
start = as.Date("2018-06-04")
stop = as.Date("2018-10-22")
persist_2018 <- persistenceForecast(start, stop, n_days, run_space, obs)
rmse_persist_2018 <- createRmseDF(n_days, persist_2018)

rmse_persist_total <- rmse_persist_2014%>%
  mutate(Year = 2014)%>%
  full_join(rmse_persist_2016 %>% mutate (Year = 2016))%>%
  full_join(rmse_persist_2017 %>% mutate (Year = 2017))%>%
  full_join(rmse_persist_2018 %>% mutate (Year = 2018))
write.csv(rmse_persist_total,"../DO_modeling_results/rmse_persist_23Mar20.csv")

rmse_persist_total%>%
  filter(Year!=2017)%>%
  ggplot(aes(x = n, y = val, col = as.factor(Year)))+
  geom_point()+
  ylab("RMSE")+
  xlab("Days past forecast generation")+
  labs(color = "Year")
```

```{r}
rmse_comb <- rmse_persist_total%>%
  mutate(Model = "persistance")%>%
  full_join(rmse_total %>% mutate(Model = "forecast"))

rmse_comb %>%
  filter(Year!=2017)%>%
  ggplot(aes(x = n, y = val, color = Model, shape = as.factor(Year)))+
  geom_point()+
  ylab("RMSE")+
  xlab("Days past forecast generation")+
  labs(shape = "Year")
```


SKIP: this would plot parameter values over 
#```{r}
plot(inputs_2016$Date,inputs_2016$Chla, )


start = as.Date("2016-06-01")
stop = as.Date("2016-10-07")
inputs_2016 <- inputs_year(start,stop)
today <- start
dir.create("../DO_modeling_figures/3Mar20/2016_param")
setwd("../DO_modeling_figures/3Mar20/2016_param")
png(file="example%02d.png", width=480, height=480)
while(today < stop){
  est2016 <- run_do_hindcast(inputs_2016, obs, today)
  plot_param(est2016, 1)
  plot_param(est2016, 2)
  plot_param(est2016, 3)
  plot_param(est2016, 4)
  plot_param(est2016, 5)
  today <- today+2
}
#```

Saving the best dates for the start and end of each season
```{r}
start = as.Date("2013-04-30")
stop = as.Date("2013-08-08")
start = as.Date("2014-06-02")
stop = as.Date("2014-10-15")
start = as.Date("2015-06-08")
stop = as.Date("2015-09-28")
start = as.Date("2016-06-01")
stop = as.Date("2016-10-07")
start = as.Date("2017-06-28")
stop = as.Date("2017-07-12")
start = as.Date("2018-06-04")
stop = as.Date("2018-10-22")
start = as.Date("2019-06-03")
stop = as.Date("2019-10-30")
```


Just for troubleshooting:
```{r}
n_en = n_en
start = start
stop = stop
time_step = "days"
obs_file = obs
driver_file = model_inputs
n_states_est = 1
n_params_est = 4
n_params_obs = 0
n_drivers = 6
parm_init = parms
obs_cv = obs_cv
param_cv = param_cv
driver_cv = driver_cv
init_cond_cv = init_cond_cv
```

Notes for next steps: 
Informed priors for parameters (there are points where r20 = -20)
Make it so that the kalman filter only runs when there's an observation -- the idea of comparing it to 0 seems v sketch???
Quantify uncertainty at each time step
Run for other years