---
title: "DO Model Hindcasting"
author: "Abby Lewis"
date: "12/8/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readxl)
library(tidyverse)
library(zoo)
library(deSolve)
library(lubridate)
library(formatR)
library(knitr)
source('EnKF_functions_05Apr20_uncert.R')
source('DO_forecasting_functions_05Apr20.R')
source('O2_models_24Mar20.R')
library(magick)
library(animation)
library(Metrics)
```

Created 20 March 20 to convert my model to a forecasting framework
- NOTE: got rid of the flexible hypo volume. I think that's what was destroying 2016
- NOTE: I am saying data collected on the day of the forecast DOES get incorporated into the forecast
- This one script can do normal, temp, o2, sss, and persistence forecasts, and it can do every type of uncertainty

To do:
- Formalize parameter selection procedure
- Check observation error
- Research oxygen max
- Think about forecast story
- Talk to Quinn about best practices for archiving forecast runs. Do I need to save all drivers/parameters/etc from each run?
- Look at alternative null models. I really think the most informative in my mind would be someone pointing at the graph and saying where they think it will go. Is this a thing?

Done:
- Set aside some data as test (2013, 2015, 2019) and some as training (2014, 2016, 2017, 2018): DONE
- Create one forecast half way through 2014: DONE
- Create forecasts for all of 2014: DONE
- Create forecasts for all training years: DONE
- Set this up to archive everything in github: DONE!!
- Calculate RMSE a certain number of days out DONE
- Plot of rmse vs the number of days away, colors for the year DONE
- Archive forecasts DONE
- Create persistence forecast DONE
- Compare RMSE with the persistence forecast to the actual model DONE
- Create forecast with just temp DONE
- Create forecast with just O2 DONE
- Add temp and o2 models to this script DONE
- Just SSS model DONE
- Compare models on a graph DONE
- READ about forecast evaluation DONE
- Look at oxygenation file for 2016 and 2018
- Finished driver, init cond, param uncertainty!
- Conclusion: Observation uncertainty is not a thing. Models need to be different already to get adjusted by enkf
- Made graphs of partitioned uncertainty as a function of forecast horizon and day of summer for each year DONE
- Standardize graphs by the amount of error DONE
- Make uncertainty calculations only based on forecasts (not model) DONE
- Add process error DONE
- Present parameters in shiny app DONE
- Linear regression of temperatures for each training year, use average DONE
- Run forecasts in Bayes model (training data) to get parameter values DONE



## Parameters, CV, number of ensembles
```{r}
## Parameters
parms <- c(
  R20 = .7, #mg/L/day
  theta = 1.12, 
  ko2 = .5, #mg/L
  sss_scalar = 3
)

#BEST YET: R20=.7, theta=1.12, ko2 = .5, sss_scalar = 3: 2016 max = 2.2, 2014 max = 1.02, 2018 max = .76
#--> Overfit to 2014, 2016 and 2018!
#R20=.6, theta=1.1, ko2 = .5, sss_scalar = 3: 2016 max = 2.24, 2014 max = 1.07
#R20=.6, theta=1.08, ko2 = .5, sss_scalar = 3: 2016 max = 2.5, 2014 max = 1.2
#R20=.5, theta=1.08, ko2 = .5, sss_scalar = 3: 2016 max = 2.42, 2014 max = 1.16
#R20=.7, theta=1.12, ko2 = .5, sss_scalar = 3: 2016 max = 2.22, 2014 max = 1.09, 2018 max = .89
#R20 = .4, theta = 1.08, ko2 = .5, sss_scalar = 4: 2016 is especially bad (2.5). 2014 is not great. 2013 is good

# From GLEON workshop 
# I made all of these up more or less randomly. Not sure how I should have come up with them
n_en = 100 # number of ensembles 
# coefficient of variation (CV) as a representation of uncertainty 
param_cv = c(R20 = .1,
             theta = .01,
             ko2 = .1,
             sss_scalar = .1)
driver_cv = c(SSS = .2,
              temp = .1,
              o2_mgL = 0) # Coefficient of variation of driver data 
init_cond_cv = 0.05
proc_sd <- 0.1 #Calculated below (last code chunk)
obs_cv = 0.05
```


```{r}
#Create observations dataframe
CTD <- read.csv("../DO_modeling_data/vol_weighted_do_fcr.csv")
CTD = CTD%>%
  filter(hypoVolume>0,
         !is.na(Conc))%>%
  mutate(Date = as.Date(Date))
obs <- CTD %>%
  filter(!is.na(Conc))%>%
  select(Date, Conc)%>%
  rename(datetime = Date)%>%
  group_by(datetime)%>%
  summarize(O2_mgL = mean(Conc))

mean_hypo_ratio <- mean(CTD$SA_m2/CTD$hypoVolume)
median_hypo_ratio <- median(CTD$SA_m2/CTD$hypoVolume)

#Create driver data frame (called model_inputs)
SSS <- read_excel("../DO_modeling_data/Calc_HOX_flow_DO_20190320.xlsx") 
SSS$time <- as.Date(SSS$time)
  
#start_all = as.Date(c("2013-05-30","2014-06-02","2015-05-28","2016-06-01","2017-06-28","2018-06-04","2019-06-03"))
#stop_all = as.Date(c("2013-09-25","2014-10-04","2015-09-28","2016-09-30","2017-07-12","2018-10-22","2019-10-30"))
#write.csv(data.frame(start_all,stop_all),"../DO_modeling_data/start_stop.csv")
start_stop <- read.csv("../DO_modeling_data/start_stop.csv")
start_all = as.Date(start_stop$start_all)
stop_all = as.Date(start_stop$stop_all)
avgs <- calc_avg(start_all,stop_all,CTD,SSS)
avg_temp<-unlist(avgs[1])
avg_o2<-unlist(avgs[2])
avg_hypoVolume<-unlist(avgs[3])
CTD$hypoVolume<-avg_hypoVolume

```


Testing: keep only training years!
```{r}
temp_slope = 0.03937878
#2013
start = start_all[year(start_all)==2013]
stop = stop_all[year(stop_all)==2013]
inputs_2013 <- inputs_year(start,stop,CTD,SSS)
test_2013 <- run_do_hindcast(inputs_2013,obs,stop-40)
plot_o2(test_2013,stop,start,stop)
plot(inputs_2013$Date,inputs_2013$Temp)
lm1 <- lm(inputs_2013$Temp~inputs_2013$Date)
#plot_hindcast(test_2013)
#pairs(inputs_2013)

#2014
start = start_all[year(start_all)==2014]
stop = stop_all[year(stop_all)==2014]
inputs_2014 <- inputs_year(start,stop,CTD,SSS)
test_2014 <- run_do_hindcast(inputs_2014,obs,stop)
plot_o2(test_2014,stop,start,stop)
lm2 <- lm(inputs_2014$Temp~inputs_2014$Date)
#plot(inputs_2014$Date,inputs_2014$Temp)
#plot_hindcast(test_2014)
#plot(inputs_2014$Date,inputs_2014$Chla)

#2015
start = start_all[year(start_all)==2015]
stop = stop_all[year(stop_all)==2015]
inputs_2015 <- inputs_year(start,stop,CTD,SSS)
test_2015 <- run_do_hindcast(inputs_2015,obs,stop)
plot_o2(test_2015,stop,start,stop)
#plot_hindcast(test_2015)
plot(inputs_2015$Date,inputs_2015$scfm)
lm3 <- lm(inputs_2015$Temp~inputs_2015$Date)

#2016
start = start_all[year(start_all)==2016]
stop = stop_all[year(stop_all)==2016]
inputs_2016 <- inputs_year(start,stop,CTD,SSS)
test_2016 <- run_do_hindcast(inputs_2016,obs,stop)
plot_o2(test_2016,stop,start,stop)
#plot_hindcast(test_2016)
plot(inputs_2016$Date,inputs_2016$Temp)
lm4 <- lm(inputs_2016$Temp~inputs_2016$Date)

#2017
start = start_all[year(start_all)==2017]
stop = stop_all[year(stop_all)==2017]
inputs_2017 <- inputs_year(start,stop,CTD,SSS)
test_2017 <- run_do_hindcast(inputs_2017,obs,stop)
plot_o2(test_2017,stop,start,stop)
#plot_hindcast(test_2017)
#plot(inputs_2017$Date,inputs_2017$Temp)
temp_slope <- mean(c(lm1$coefficients[2],lm2$coefficients[2],lm3$coefficients[2],lm4$coefficients[2]))
```




Run forecasts!
```{r}
#for(uncert in c("param","all","init","proc","driver")){ 
for(model_name in c("full","temp","o2","SSS")){ 
  run_space <- 1 #Number of days between runs of the model
  n_days <- 14 #Forecast horizon
  #model_name = "full" #Options for model_name: SSS, temp, o2, full. SSS is no temp no o2, O2 is no temp. Temp is no o2.
  gif = T
  uncert = "all" #Options = "all","init","driver","param","proc"
  date <- format(Sys.Date(),"%d%b%y")
  
  #2013
  start = start_all[year(start_all)==2013]
  stop = stop_all[year(stop_all)==2013]
  results_2013 <- runForecasts(start, stop, n_days, run_space, obs, delay = 5, model_name = model_name, gif = gif,avg_o2 = avg_o2,avg_temp=avg_temp,uncert = uncert)
  dir.create(paste("../DO_modeling_results/",date,sep = ""))
  write.csv(results_2013,paste("../DO_modeling_results/",date,"/forecast_2013_",model_name,"_model_",uncert,"_uncert.csv", sep = ""))
  rmse_2013_filt <- createRmseDF_filt(n_days, results_2013, obs) # Calculate rmse for days where there was an observation
  rmse_2013 <- createRmseDF(n_days, results_2013) # Calculate rmse for all days
  rmse_2013
  rmse_2013_filt
  
  #2014
  start = start_all[year(start_all)==2014]
  stop = stop_all[year(stop_all)==2014]
  results_2014 <- runForecasts(start, stop, n_days, run_space, obs, delay = 5, model_name = model_name, gif = gif,avg_o2 = avg_o2,avg_temp=avg_temp,uncert = uncert)
  write.csv(results_2014,paste("../DO_modeling_results/",date,"/forecast_2014_",model_name,"_model_",uncert,"_uncert.csv", sep = ""))
  rmse_2014_filt <- createRmseDF_filt(n_days, results_2014, obs) # Calculate rmse for days where there was an observation
  rmse_2014 <- createRmseDF(n_days, results_2014) # Calculate rmse for all days
  rmse_2014
  rmse_2014_filt
  
  #2015
  start = start_all[year(start_all)==2015]
  stop = stop_all[year(stop_all)==2015]
  results_2015 <- runForecasts(start, stop, n_days, run_space, obs, delay = 5, model_name = model_name, gif = gif,avg_o2 = avg_o2,avg_temp=avg_temp,uncert = uncert)
  write.csv(results_2015,paste("../DO_modeling_results/",date,"/forecast_2015_",model_name,"_model_",uncert,"_uncert.csv", sep = ""))
  rmse_2015_filt <- createRmseDF_filt(n_days, results_2015, obs)
  rmse_2015 <- createRmseDF(n_days, results_2015)
  rmse_2015
  rmse_2015_filt
  
  #2016
  start = start_all[year(start_all)==2016]
  stop = stop_all[year(stop_all)==2016]
  results_2016 <- runForecasts(start, stop, n_days, run_space, obs, delay = 5, model_name = model_name, gif = gif,avg_o2 = avg_o2,avg_temp=avg_temp,uncert = uncert)
  write.csv(results_2016,paste("../DO_modeling_results/",date,"/forecast_2016_",model_name,"_model_",uncert,"_uncert.csv", sep = ""))
  rmse_2016_filt <- createRmseDF_filt(n_days, results_2016, obs)
  rmse_2016 <- createRmseDF(n_days, results_2016)
  rmse_2016
  rmse_2016_filt
  
  #2017
  start = start_all[year(start_all)==2017]
  stop = stop_all[year(stop_all)==2017]
  results_2017 <- runForecasts(start, stop, n_days, run_space, obs, delay = 30, model_name = model_name, gif = gif,avg_o2 = avg_o2,avg_temp=avg_temp,uncert = uncert)
  write.csv(results_2017,paste("../DO_modeling_results/",date,"/forecast_2017_",model_name,"_model_",uncert,"_uncert.csv", sep = ""))
  rmse_2017_filt <- createRmseDF_filt(n_days, results_2017,obs)
  rmse_2017 <- createRmseDF(n_days, results_2017)
  
  #2018
  start = start_all[year(start_all)==2018]
  stop = stop_all[year(stop_all)==2018]
  results_2018 <- runForecasts(start, stop, n_days, run_space, obs, delay = 5, model_name = model_name, gif = gif,avg_o2 = avg_o2,avg_temp=avg_temp,uncert = uncert)
  write.csv(results_2018,paste("../DO_modeling_results/",date,"/forecast_2018_",model_name,"_model_",uncert,"_uncert.csv", sep = ""))
  rmse_2018_filt <- createRmseDF_filt(n_days, results_2018,obs)
  rmse_2018 <- createRmseDF(n_days, results_2018)
  rmse_2018
  rmse_2018_filt
  
  #2019
  start = start_all[year(start_all)==2019]
  stop = stop_all[year(stop_all)==2019]
  results_2019 <- runForecasts(start, stop, n_days, run_space, obs, delay = 5, model_name = model_name, gif = gif,avg_o2 = avg_o2,avg_temp=avg_temp,uncert = uncert)
  write.csv(results_2019,paste("../DO_modeling_results/",date,"/forecast_2019_",model_name,"_model_",uncert,"_uncert.csv", sep = ""))
  rmse_2019_filt <- createRmseDF_filt(n_days, results_2019,obs)
  rmse_2019 <- createRmseDF(n_days, results_2019)
  rmse_2019
  rmse_2019_filt
#}


  rmse_total <- rmse_2013%>%
    mutate(Year = 2013)%>%
    full_join(rmse_2014 %>% mutate (Year = 2014))%>%
    full_join(rmse_2015 %>% mutate (Year = 2015))%>%
    full_join(rmse_2016 %>% mutate (Year = 2016))%>%
    full_join(rmse_2017 %>% mutate (Year = 2017))%>%
    full_join(rmse_2018 %>% mutate (Year = 2018))%>%
    full_join(rmse_2019 %>% mutate (Year = 2019))
  date <- format(Sys.Date(),"%d%b%y")
  write.csv(rmse_total,paste("../DO_modeling_results/rmse_",model_name,"_",date,".csv", sep = ""))
  
  rmse_total_filt <- rmse_2013_filt%>%
    mutate(Year = 2013)%>%
    full_join(rmse_2014_filt %>% mutate (Year = 2014))%>%
    full_join(rmse_2015_filt %>% mutate (Year = 2015))%>%
    full_join(rmse_2016_filt %>% mutate (Year = 2016))%>%
    full_join(rmse_2017_filt %>% mutate (Year = 2017))%>%
    full_join(rmse_2018_filt %>% mutate (Year = 2018))%>%
    full_join(rmse_2019_filt %>% mutate (Year = 2019))
  date <- format(Sys.Date(),"%d%b%y")
  write.csv(rmse_total,paste("../DO_modeling_results/rmse_filt_",model_name,"_",date,".csv", sep = ""))

}

rmse_total%>%
  filter(Year!=2017)%>%
  ggplot(aes(x = n, y = val, col = as.factor(Year)))+
  geom_point()+
  ylab("RMSE (mg/L O2)")+
  xlab("Days past forecast generation")+
  labs(color = "Year")

rmse_total_filt%>%
  filter(Year!=2017)%>%
  ggplot(aes(x = n, y = val, col = as.factor(Year)))+
  geom_point()+
  ylab("RMSE (mg/L O2)")+
  xlab("Days past forecast generation")+
  labs(color = "Year")

```


```{r}
run_space <- 1 #Number of days between runs of the model
n_days <- 14 #Forecast horizon

#2013
start = start_all[year(start_all)==2013]
stop = stop_all[year(stop_all)==2013]
persist_2013 <- persistenceForecast(start, stop, n_days, run_space, obs)
rmse_persist_2013 <- createRmseDF(n_days, persist_2013)

#2014
start = start_all[year(start_all)==2014]
stop = stop_all[year(stop_all)==2014]
persist_2014 <- persistenceForecast(start, stop, n_days, run_space, obs)
rmse_persist_2014 <- createRmseDF(n_days, persist_2014)

#2015
start = start_all[year(start_all)==2015]
stop = stop_all[year(stop_all)==2015]
persist_2015 <- persistenceForecast(start, stop, n_days, run_space, obs)
rmse_persist_2015 <- createRmseDF(n_days, persist_2015)

#2016
start = start_all[year(start_all)==2016]
stop = stop_all[year(stop_all)==2016]
persist_2016 <- persistenceForecast(start, stop, n_days, run_space, obs)
rmse_persist_2016 <- createRmseDF(n_days, persist_2016)

#2017
start = start_all[year(start_all)==2017]
stop = stop_all[year(stop_all)==2017]
persist_2017 <- persistenceForecast(start, stop, n_days, run_space, obs)
rmse_persist_2017 <- createRmseDF(n_days, persist_2017)

#2018
start = start_all[year(start_all)==2018]
stop = stop_all[year(stop_all)==2018]
persist_2018 <- persistenceForecast(start, stop, n_days, run_space, obs)
rmse_persist_2018 <- createRmseDF(n_days, persist_2018)

#2019
start = start_all[year(start_all)==2019]
stop = stop_all[year(stop_all)==2019]
persist_2019 <- persistenceForecast(start, stop, n_days, run_space, obs)
rmse_persist_2019 <- createRmseDF(n_days, persist_2019)

rmse_persist_total <- rmse_persist_2013%>%
  mutate(Year = 2013)%>%
  full_join(rmse_persist_2014 %>% mutate (Year = 2014))%>%
  full_join(rmse_persist_2015 %>% mutate (Year = 2015))%>%
  full_join(rmse_persist_2016 %>% mutate (Year = 2016))%>%
  full_join(rmse_persist_2017 %>% mutate (Year = 2017))%>%
  full_join(rmse_persist_2018 %>% mutate (Year = 2018))%>%
  full_join(rmse_persist_2019 %>% mutate (Year = 2019))
date <- format(Sys.Date(),"%d%b%y")
write.csv(rmse_persist_total,paste("../DO_modeling_results/rmse_persist_",date,".csv", sep = ""))

rmse_persist_total%>%
  filter(Year!=2017)%>%
  ggplot(aes(x = n, y = val, col = as.factor(Year)))+
  geom_point()+
  ylab("RMSE")+
  xlab("Days past forecast generation")+
  labs(color = "Year")
```

```{r}
temp <- read.csv("../DO_modeling_results/rmse_temp_21Apr20.csv")
o2 <- read.csv("../DO_modeling_results/rmse_o2_21Apr20.csv")
full <- read.csv("../DO_modeling_results/rmse_full_21Apr20.csv")
sss <- read.csv("../DO_modeling_results/rmse_sss_21Apr20.csv")
persist <- read.csv("../DO_modeling_results/rmse_persist_21Apr20.csv")

rmse_all <- persist%>%
  mutate(Model = "persistance")%>%
  full_join(full %>% mutate(Model = "full"))%>%
  full_join(o2 %>% mutate(Model = "o2"))%>%
  full_join(temp %>% mutate(Model = "temp"))%>%
  full_join(sss %>% mutate(Model = "sss"))

date <- format(Sys.Date(),"%d%b%y")
jpeg(paste("../DO_modeling_figures/",date,"/RMSE_all.jpeg",sep = ""),width = 5, height = 2, unit = "in", res = 300)
rmse_all %>%
  filter(Year!=2017)%>%
  ggplot(aes(x = n, y = val, color = Model))+
  geom_line()+
  ylab("RMSE")+
  xlab("Days past forecast generation")+
  facet_wrap("Year")
dev.off()
```

Uncertainty calcs
```{r}
#Just to get column names
all <- read.csv(paste("../DO_modeling_results/15Apr20/forecast_2013_full_model_all_uncert.csv",sep = ""))
SDs = all[FALSE,seq(31,44)] #This says SD but it is actually var throughout

#Run through all saved forecasts
for(year in seq(2013,2019)){
  full <- read.csv(paste("../DO_modeling_results/15Apr20/forecast_",year,"_full_model_all_uncert.csv",sep = ""))%>%
    mutate(uncert = "all",
           year = year)
  full_var <- sd_sum(full,"all",year)
  param <- read.csv(paste("../DO_modeling_results/15Apr20/forecast_",year,"_full_model_param_uncert.csv",sep = ""))%>%
    mutate(uncert = "param",
           year = year)
  param_var <- sd_sum(param,"param",year)
  driver <- read.csv(paste("../DO_modeling_results/15Apr20/forecast_",year,"_full_model_driver_uncert.csv",sep = ""))%>%
    mutate(uncert = "driver",
           year = year)
  driver_var <- sd_sum(driver,"driver",year)
  init <- read.csv(paste("../DO_modeling_results/15Apr20/forecast_",year,"_full_model_init_uncert.csv",sep = ""))%>%
    mutate(uncert = "init",
           year = year)
  init_var <- sd_sum(init,"init",year)
  proc <- read.csv(paste("../DO_modeling_results/15Apr20/forecast_",year,"_full_model_proc_uncert.csv",sep = ""))%>%
    mutate(uncert = "proc",
           year = year)
  proc_var <- sd_sum(proc,"proc",year)
  SDs = SDs%>%
    full_join(full_var)%>%
    full_join(param_var)%>%
    full_join(driver_var)%>%
    full_join(init_var)%>%
    full_join(proc_var)
  all = all%>%
    full_join(full)%>%
    full_join(param)%>%
    full_join(driver)%>%
    full_join(init)%>%
    full_join(proc)
}

all_sd = all[,c(2,seq(31,46))]%>%
  filter(!is.na(TODAY))

all_sd_std = all_sd%>%
  filter(uncert !="all")%>%
  group_by(TODAY)%>%
  mutate(TOTAL_7 = sum(PLUS7_var),
         TOTAL_14 = sum(PLUS14_var))
```

```{r}
toCalcProcUncert <- all %>%
  filter(year(as.Date(TODAY))<=2017,
         uncert == "all")
n <- seq(1,n_days)
output_df <- data.frame(n)
results <- toCalcProcUncert
results <- as.data.frame(results)
for(i in seq(1:n_days)){
  predicted <- results[i+2]
  observed <- results[i+2+n_days]
  output_df$mean[output_df$n == i] <- mean(observed[!is.na(observed)] - predicted[!is.na(observed)])
  output_df$sd[output_df$n == i] <- sd(observed[!is.na(observed)] - predicted[!is.na(observed)])
}
output_df
lm(output_df$mean~output_df$n)
```


Uncertainty plots
- NOTE: warnings about missing data are not a problem! Confirmed that these are just the NAs at the end of the summer
  - 13*7 = 91
  - 6*7 = 42
  - 91*3 = 273
  - 42*3 = 126
```{r}

png("../DO_modeling_figures/15Apr20/uncert_fract7.png",width = 6, height = 4, units = "in", res = 300)
all_sd_std %>%
  filter(uncert != "all")%>%
  ggplot(aes(x = as.Date(TODAY),y= PLUS7_var/TOTAL_7, fill = uncert))+
  geom_bar(stat = "identity", width = 1)+
  facet_wrap("year", scales = "free_x")+
  labs(fill = "Uncertainty")+
  xlab("")+
  ylab("Variance (fraction of total)")+
  ggtitle("7 day horizon")
dev.off()

png("../DO_modeling_figures/15Apr20/uncert_fract14.png",width = 6, height = 4, units = "in", res = 300)
all_sd_std %>%
  filter(uncert != "all")%>%
  ggplot(aes(x = as.Date(TODAY),y= PLUS14_var/TOTAL_14, fill = uncert))+
  geom_bar(stat = "identity", width = 1)+
  facet_wrap("year", scales = "free_x")+
  labs(fill = "Uncertainty")+
  xlab("")+
  ylab("Variance (fraction of total)")+
  ggtitle("14 day horizon")
dev.off()

png("../DO_modeling_figures/15Apr20/uncert_season7.png",width = 6, height = 4, units = "in", res = 300)
all_sd %>%
  filter(uncert != "all")%>%
  ggplot(aes(x = as.Date(TODAY),y= PLUS7_var, fill = uncert))+
  geom_bar(stat = "identity", width = 1)+
  facet_wrap("year", scales = "free_x")+
  scale_fill_discrete(name = "Uncertainty", limits = c("driver","init","param","proc"), 
                      labels = c("driver","initial cond","parameter","process"))+
  xlab("")+
  ylab("Variance (7 day horizon)")+
  geom_line(aes(x = as.Date(TODAY), y = PLUS7_var, lty=uncert), data = all_sd %>% filter(uncert == "all"))+
  scale_linetype_discrete(name = "",labels = c("all"))
dev.off()

png("../DO_modeling_figures/15Apr20/uncert_season14.png",width = 6, height = 4, units = "in", res = 300)
all_sd %>%
  filter(uncert != "all", year!=2017)%>%
  ggplot(aes(x = as.Date(TODAY),y= PLUS14_var, fill = uncert))+
  geom_bar(stat = "identity", width = 1)+
  facet_wrap("year", scales = "free_x")+
  scale_fill_discrete(name = "Uncertainty", limits = c("driver","init","param","proc"), 
                      labels = c("driver","initial cond","parameter","process"))+
  xlab("")+
  ylab("Variance (14 day horizon)")+
  geom_line(aes(x = as.Date(TODAY), y = PLUS14_var, lty=uncert), data = all_sd %>% filter(uncert == "all", year !=2017))+
  scale_linetype_discrete(name = "",labels = c("all"))
dev.off()

SDs_final = SDs%>%
  gather(day,var,1:14)%>%
  mutate(day_n = as.numeric(gsub("_var",gsub("PLUS",day,replacement = ""),replacement = "")))%>%
  select(-day)

png("../DO_modeling_figures/15Apr20/uncert_horiz.png",width = 6, height = 4, units = "in", res = 300)
SDs_final%>%
  filter(uncert != "all")%>%
  ggplot(aes(x = day_n,y=var, fill = uncert))+
  geom_bar(stat = "identity")+
  facet_wrap("year")+
  scale_fill_discrete(name = "Uncertainty", limits = c("driver","init","param","proc"), 
                      labels = c("driver","initial cond","parameter","process"))+
  xlab("Forecast Horizon (days)")+
  ylab("Variance")+
  geom_line(aes(x = day_n, y = var, lty=uncert), data = SDs_final %>% filter(uncert == "all"))+
  scale_linetype_discrete(name = "",labels = c("all"))
dev.off()
```


SKIP: this would plot parameter values over time
#```{r}
plot(inputs_2016$Date,inputs_2016$Chla, )


start = as.Date("2016-06-01")
stop = as.Date("2016-10-07")
inputs_2016 <- inputs_year(start,stop)
today <- start
dir.create("../DO_modeling_figures/3Mar20/2016_param")
setwd("../DO_modeling_figures/3Mar20/2016_param")
png(file="example%02d.png", width=480, height=480)
while(today < stop){
  est2016 <- run_do_hindcast(inputs_2016, obs, today)
  plot_param(est2016, 1)
  plot_param(est2016, 2)
  plot_param(est2016, 3)
  plot_param(est2016, 4)
  plot_param(est2016, 5)
  today <- today+2
}
#```

Just for troubleshooting:
```{r}
n_en = n_en
start = start
stop = min(stop,today+n_days)
time_step = "days"
obs_file = obs
driver_file = model_inputs
n_states_est = 1
n_params_est = 4
n_params_obs = 0
n_drivers = 2
parm_init = parms
obs_cv = obs_cv2
param_cv = param_cv2
driver_cv = driver_cv2
init_cond_cv = init_cond_cv2
model = O2_model
```

Notes for next steps: 
Informed priors for parameters (there are points where r20 = -20)
Make it so that the kalman filter only runs when there's an observation -- the idea of comparing it to 0 seems v sketch???
Quantify uncertainty at each time step
Run for other years