---
title: "DO Model Hindcasting"
author: "Abby Lewis"
date: "12/8/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readxl)
library(tidyverse)
library(zoo)
library(deSolve)
library(lubridate)
library(formatR)
library(knitr)
source('EnKF_functions_21Mar20.R')
library(magick)
library(animation)
```

Created 20 March 20 to convert my model to a forecasting framework
What I want is 14 days of predictions starting from the date of the forecast
- Before those 14 days it can work just as normal, assimilating data, etc
- I do need an estimation of uncertainty at all of those points
- Do I run this every day? Seem like there's not really a point given that there won't be any new driver data/data assimilation
- Maybe every week for now?
- NOTE: got rid of the flexible hypo volume. I think that's what was destroying 2016

First steps:
- Set aside some data as test (2013, 2015, 2019) and some as training (2014, 2016, 2017, 2018): DONE
- Create one forecast half way through 2014: DONE
- Create forecasts for all of 2014: DONE
- Create forecasts for all training years: DONE
- Set this up to archive everything in github: DONE!!
- Need a way of quantifying how good the model is
  - Dataframe where rows are the date the model was run and columns are the dates of the summer, and each cell is the prediction, and then one row with the actual observations?
  - Calculate RMSE a certain number of days out
  - Plot of rmse vs the number of days away, colors for the year
- Start comparing different models


## Model
```{r}

O2_model <- function(times, states, parms, inputs){
  
  #STATES 
  O2_mgL <- states[1]

  #PARMS 
  R20 <- as.numeric(parms[1])
  theta <- as.numeric(parms[2])
  ko2 <- as.numeric(parms[3])
  sss_scalar <- as.numeric(parms[4])
  k_chla <- as.numeric(parms[5])
  
  #INPUT
  SSS <- inputs[1]
  temp <- inputs[2]
  chla <- inputs[3]
  
  #CALCULATIONS
  R = R20*theta^(temp-20)*O2_mgL/(O2_mgL+ko2)
  scalar = 1
  if(SSS>0){
    scalar = sss_scalar
  }
  OD = R*scalar

  #DERIVATIVE
  dO2_mgLdt <- SSS-OD

  #RETURN A LIST OF THE DERIVATIVES
  return(list(c(dO2_mgLdt), c(parms)))
}
```

## Parameters
```{r}
parms <- c(
  R20 = .7, #mg/L/day
  theta = 1.1, 
  ko2 = 1, #mg/L
  sss_scalar = 3
)
```

```{r} 
# From GLEON workshop 
# I made all of these up more or less randomly. Not sure how I should have come up with them


n_en = 100 # number of ensembles 
# coefficient of variation (CV) as a representation of uncertainty 
param_cv = c(R20 = .1,
             theta = .01,
             ko2 = .1,
             sss_scalar = .2)
driver_cv = c(SSS = .2,
    temp = .2) # Coefficient of variation of driver data 
init_cond_cv = .1
obs_cv = 0.05
```

```{r}
#Create observations dataframe
  CTD <- read.csv("../DO_modeling_data/vol_weighted_do_fcr.csv")
  CTD = CTD%>%
    filter(hypoVolume>0,
           !is.na(Conc))%>%
    mutate(Date = as.Date(Date))
  obs <- CTD %>%
    filter(!is.na(Conc))%>%
    select(Date, Conc)%>%
    rename(datetime = Date)%>%
    group_by(datetime)%>%
    summarize(O2_mgL = mean(Conc))
  CTD$hypoVolume<-mean(CTD$hypoVolume, na.rm = TRUE)
  
  mean_hypo_ratio <- mean(CTD$SA_m2/CTD$hypoVolume)
  median_hypo_ratio <- median(CTD$SA_m2/CTD$hypoVolume)
  
#Create driver data frame (called model_inputs)
  SSS <- read_excel("../DO_modeling_data/Calc_HOX_flow_DO_20190320.xlsx") 
  SSS$time <- as.Date(SSS$time)
```


```{r}
inputs_year<- function(start, stop){
  dates = data.frame(seq(start,stop,by = "days"))
  colnames(dates) <- "Date"
  inputs = dates %>%
    left_join(CTD %>%
                dplyr::select(Date,Conc,Temp,hypoVolume,thermo_depth,Chla_ugL,SA_m2), by = "Date")%>%
    left_join(SSS %>% 
                dplyr::select(time, scfm), by = c("Date"="time"))%>%
    arrange(Date)
  if(all(is.na(inputs$Chla_ugL))){
    inputs$Chla_ugL<-1
  }
  inputs = inputs%>%
    group_by(Date)%>%
    summarise(Conc = mean(Conc),
              Temp = mean(Temp),
              hypoVolume = mean(hypoVolume),
              thermo_depth = mean(thermo_depth),
              scfm = mean(scfm),
              Chla = mean(Chla_ugL),
              SA = mean(SA_m2))
}

run_do_hindcast <- function(inputs, obs, today, n_days = 14){
  obs = obs%>%
    filter(datetime<=today)
  inputs = inputs%>%
    filter(Date<=stop, 
           Date>=start,
           Date<=today+n_days)
  inputs[inputs$Date > today,c(2,3,4,5,7,8)] <- NA
  inputs = inputs%>%
    mutate(Conc = na.approx(Conc, rule = 2),
           Temp = na.approx(Temp, rule = 2),
           hypoVolume = na.approx(hypoVolume, rule = 2),
           thermo_depth = na.approx(thermo_depth, rule = 2),
           scfm = ifelse(Date>=as.Date("2013-05-15"),scfm,0),
           SSS_add_conc = scfm*50*1000000/hypoVolume,
           Chla = na.approx(Chla, rule = 2),
           SA = na.approx(SA, rule = 2))
  simulation_time <- as.numeric(difftime(min(today+n_days, stop), start, unit = "days")+1) #days
  #Assemble driver data
  model_inputs <- list(datetime = inputs$Date,
    SSS = inputs$SSS_add_conc,
    temp = inputs$Temp)
  model_inputs<- data.frame(model_inputs)
  
  #Set initial conditions
  yini <- c(
    O2_mgL = inputs$Conc[inputs$Date == start]
  )

  
  #Run EnKF
  est_out = EnKF(n_en = n_en, 
           start = start,
           stop = min(stop, today+n_days),
           time_step = "days",
           obs_file = obs, 
           driver_file = model_inputs, 
           n_states_est = 1,
           n_params_est = 4,
           n_params_obs = 0,
           n_drivers = 2,
           parm_init = parms, 
           obs_cv = obs_cv,
           param_cv = param_cv,
           driver_cv = driver_cv, 
           init_cond_cv = init_cond_cv)
  return(est_out)
}

plot_hindcast <- function(est_out){
  par(mfrow = c(2,3))
  param_names = c("R20","theta","ko2","sss_scalar","chla_vmax")
  plot_param = function(est_out,num,name = "Parameter value"){
    num = num+1
    mean_param_est = apply(est_out$Y[num,,], 1, FUN = mean)
    plot(mean_param_est ~ est_out$dates, type ='l', 
         ylim = range(est_out$Y[num,,]),
         col = 'grey', ylab = name, xlab ='', main = param_names[num-1])
    for(i in 2:n_en){
      lines(est_out$Y[num,,i] ~ est_out$dates, col = 'grey')
    }
    lines(mean_param_est ~ est_out$dates, col = 'black', lwd = 2)
  }
  for(i in seq(1,length(param_names))){
    plot_param(est_out,i)
  }
}


plot_o2 = function(est_out, today, start, stop){
  mean_o2_est = apply(est_out$Y[1,,], 1, FUN = mean)
  plot(mean_o2_est ~ est_out$dates, type ='l', 
       ylim = c(-1,25),#max(c(est_out$Y[1,,], est_out$obs[1,,]),na.rm = T)),
       col = 'grey', ylab = 'O2 (mg L-1)', xlab = '',main = year(est_out$dates[1]), xlim = c(start, stop))
  for(i in 2:n_en){
    lines(est_out$Y[1,,i] ~ est_out$dates, 
          col = 'grey')
  }
  lines(mean_o2_est ~ est_out$dates, col = 'black', lwd =2 )
  future_obs <- obs[obs$datetime>today&obs$datetime<=(today+14),]
  obs <- obs[obs$datetime<=today,]
  points(obs$O2_mgL~obs$datetime, pch = 16, col = rgb(1,0,0))
  points(future_obs$O2_mgL~future_obs$datetime, pch = 16, col = rgb(0,0,1))
  abline(v = today)
  #arrows(est_out$dates, est_out$obs[1,,] - 
   #        est_out$state_sd, 
    #     est_out$dates, est_out$obs[1,,] +
     #      est_out$state_sd, 
      #   code = 3, length = 0.1, angle = 90, col = 'red')
}

plot_param = function(est_out,num,name = "Parameter value"){
  num = num+1
  mean_param_est = apply(est_out$Y[num,,], 1, FUN = mean)
  plot(mean_param_est ~ est_out$dates, type ='l', 
       ylim = range(est_out$Y[num,,]),
       col = 'grey', ylab = name, xlab ='', main = year(est_out$dates[1]))
  for(i in 2:n_en){
    lines(est_out$Y[num,,i] ~ est_out$dates, col = 'grey')
  }
  lines(mean_param_est ~ est_out$dates, col = 'black', lwd = 2)
}
```

```{r}
#simulation_time <- as.numeric(difftime(today+n_days, start, unit = "days")+1)
start = as.Date("2014-06-02")
stop = as.Date("2014-10-15")
inputs_2014 <- inputs_year(start,stop)
today <- start
dir.create("../DO_modeling_figures/3Mar20/2014")
setwd("../DO_modeling_figures/3Mar20/2014")
png(file="example%02d.png", width=480, height=480)
while(today < stop){
  est2014 <- run_do_hindcast(inputs_2014, obs, today)
  plot_o2(est2014, today, start, stop)
  today <- today+7
}
# Use image magick
#setwd("../DO_modeling_figures/3Mar20/2014") #You need to run this if and only if you haven't run the setwd() line above
system("convert -delay 30 *.png animated_count_down.gif")
dev.off()
# Remove png files
#file.remove(list.files(pattern=".png"))
```

```{r}
#simulation_time <- as.numeric(difftime(today+n_days, start, unit = "days")+1)
start = as.Date("2016-06-01")
stop = as.Date("2016-10-07")
inputs_2016 <- inputs_year(start,stop)
today <- start
dir.create("../DO_modeling_figures/3Mar20/2016")
setwd("../DO_modeling_figures/3Mar20/2016")
png(file="example%02d.png", width=480, height=480)
while(today < stop){
  est2016 <- run_do_hindcast(inputs_2016, obs, today)
  plot_o2(est2016, today, start, stop)
  today <- today+7
}
# Use image magick
#setwd("../DO_modeling_figures/3Mar20/2016") #You need to run this if and only if you haven't run the setwd() line above
system("convert -delay 30 *.png animated_count_down.gif")
dev.off()
# Remove png files
#file.remove(list.files(pattern=".png"))

```

SKIP
#```{r}
plot(inputs_2016$Date,inputs_2016$Chla, )


start = as.Date("2016-06-01")
stop = as.Date("2016-10-07")
inputs_2016 <- inputs_year(start,stop)
today <- start
dir.create("../DO_modeling_figures/3Mar20/2016_param")
setwd("../DO_modeling_figures/3Mar20/2016_param")
png(file="example%02d.png", width=480, height=480)
while(today < stop){
  est2016 <- run_do_hindcast(inputs_2016, obs, today)
  plot_param(est2016, 1)
  plot_param(est2016, 2)
  plot_param(est2016, 3)
  plot_param(est2016, 4)
  plot_param(est2016, 5)
  today <- today+2
}
#```

```{r}
#simulation_time <- as.numeric(difftime(today+n_days, start, unit = "days")+1)
start = as.Date("2017-06-28")
stop = as.Date("2017-07-12")
inputs_2017 <- inputs_year(start,stop)
today <- start
dir.create("../DO_modeling_figures/3Mar20/2017")
setwd("../DO_modeling_figures/3Mar20/2017")
png(file="example%02d.png", width=480, height=480)
while(today < stop){
  est2017 <- run_do_hindcast(inputs_2017, obs, today)
  plot_o2(est2017, today, start, stop)
  today <- today+1
}
# Use image magick
#setwd("../DO_modeling_figures/3Mar20/2014") #You need to run this if and only if you haven't run the setwd() line above
system("convert -delay 20 *.png animated_count_down.gif")
dev.off()
# Remove png files
#file.remove(list.files(pattern=".png"))
```

```{r}
#simulation_time <- as.numeric(difftime(today+n_days, start, unit = "days")+1)
start = as.Date("2018-06-04")
stop = as.Date("2018-10-22")
inputs_2018 <- inputs_year(start,stop)
today <- start
dir.create("../DO_modeling_figures/3Mar20/2018")
setwd("../DO_modeling_figures/3Mar20/2018")
png(file="example%02d.png", width=480, height=480)
while(today < stop){
  est2018 <- run_do_hindcast(inputs_2018, obs, today)
  plot_o2(est2018, today, start, stop)
  today <- today+7
}
# Use image magick
#setwd("../DO_modeling_figures/3Mar20/2018") #You need to run this if and only if you haven't run the setwd() line above
system("convert -delay 30 *.png animated_count_down.gif")
dev.off()
# Remove png files
#file.remove(list.files(pattern=".png"))
```

```{r}
start = as.Date("2013-04-30")
stop = as.Date("2013-08-08")
start = as.Date("2014-06-02")
stop = as.Date("2014-10-15")
start = as.Date("2015-06-08")
stop = as.Date("2015-09-28")
start = as.Date("2016-06-01")
stop = as.Date("2016-10-07")
start = as.Date("2017-06-28")
stop = as.Date("2017-07-12")
start = as.Date("2018-06-04")
stop = as.Date("2018-10-22")
start = as.Date("2019-06-03")
stop = as.Date("2019-10-30")
```


Just for troubleshooting:
```{r}
n_en = n_en
start = start
stop = stop
time_step = "days"
obs_file = obs
driver_file = model_inputs
n_states_est = 1
n_params_est = 4
n_params_obs = 0
n_drivers = 6
parm_init = parms
obs_cv = obs_cv
param_cv = param_cv
driver_cv = driver_cv
init_cond_cv = init_cond_cv
```

Notes for next steps: 
Informed priors for parameters (there are points where r20 = -20)
Make it so that the kalman filter only runs when there's an observation -- the idea of comparing it to 0 seems v sketch???
Quantify uncertainty at each time step
Run for other years