---
title: "Shiny"
author: "Abby Lewis"
date: "4/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Load packages
library(shiny)
library(shinythemes)
library(tidyverse)
library(readr)
library(lubridate)
library(readxl)
library(Metrics)
```


A shiny app to get expert predictions as a null model
Created by ASL 
April 2020

TO DO
- Paired test comparing people to the model at each point
- Deal with the connection between lines/put back people's previous guesses
- Add grey dotted lines for oxygenation changes
- Why the flash of data when you switch years
- Have people input full name to start
- Set up intervals that it progressively moves through


DONE
- Set up a plot to take predictions. Only include observation (no model) 
- Get shiny to record point clicks
- Add a button to reset
- Plot oxygenation in a figure below
- People need to click on today to make their prediction (within some interval). If not exact, adjust to exact
- Add a button to submit forecast (bonus if this is a popup)
- When people submit forecasts, the future observations show up
- Automatically stop when they reach 14 days
- Get fancy with what is allowed: don't allow cursor to double back
- Set up a database to store point clicks/hover
- Set up a widget to show people's RMSE
- Don't show the whole season (but do show the past)
- Mixed manager-model option (archive full model and display)



#```{r}
x<-as.Date("2019-08-01")
y<-10
initials <- "TEST"
TODAY <- as.Date("2019-08-01")
time_created <- Sys.time()
human_model <- data.frame(TODAY,x,y,initials,time_created)

write_csv(human_model,"human_forecasts.csv")
#```



```{r, include=FALSE}
start_stop <- read.csv("start_stop.csv") #load start and end dates for the stratified period of each summer
start = as.Date(start_stop$start_all) #format as date
stop = as.Date(start_stop$stop_all)
year<-2019 #initial year is 2019

CTD <- read.csv("../DO_modeling_data/vol_weighted_do_fcr.csv") #load observations
obs = CTD%>%
  filter(hypoVolume>0,
         !is.na(Conc))%>% 
  mutate(Date = as.Date(Date)) %>%
  select(Date, Conc)%>%
  rename(datetime = Date)%>%
  group_by(datetime)%>%
  summarize(O2_mgL = mean(Conc)) #create a dataframe with dates and oxygen measurements, with only one measurement per day

temp = CTD %>%
  filter(hypoVolume>0,
         !is.na(Conc))%>%
  mutate(Date = as.Date(Date)) %>%
  select(Date, Temp)%>%
  rename(datetime = Date)%>%
  group_by(datetime)%>%
  summarize(Temp = mean(Temp)) #create a dataframe with dates and temperature measurements, with only one measurement per day

SSS <- read_excel("../DO_modeling_data/Calc_HOX_flow_DO_20190320.xlsx") #load oxygenation data
SSS$time <- as.Date(SSS$time)

# Define UI
# UI is composed of a title panel, a side panel (left), and a main panel. This function says where everything should go, and the next function actually adds the content in those locations
#Each of the inputs and outputs here will be used/created in the server function below
ui <- fluidPage(theme = shinytheme("lumen"),
  titlePanel(h1("DO forecast",align = "center")), #Add title
  sidebarPanel(
    #selectInput creates a dropdown menu with these years
    selectInput(inputId = "year", label = strong("Forecast Year"), 
                choices = c("2019","2018","2016","2015","2014","2013"),
                selected = "2019"),
    #sliderInput creates a slider that allows people to choose the date of the forecast
    sliderInput("date", strong("Forecast date"), value = min(start[year(start)==year])+14, 
              min = min(start[year(start)==year])+14, max = max(stop[year(stop)==year]), step = 1),
    #checkboxInput allows people to select whether they want to see the model or not
    checkboxInput("model","model"),
    #this actionButton allows people to reset their forecast (e.g. if they drew a forecast they didn't like)
    actionButton("reset", "reset"),
    #I am using uiOutput here instead of just having a button for the next forecast because I only want it to appear after people have submitted their forecast
    uiOutput("next_forecast"),
    #I am using uiOutput here because this is several lines of formatted text that will change depending on someone's input
    uiOutput("score_block")
  ),

    # Output: 
  mainPanel(
    plotOutput("plot", #this plot will be created below
               #this allows me to track people's mouse movements:
               hover=hoverOpts(id = "hover", delayType = "throttle", clip = TRUE, nullOutside = TRUE), 
               #this allows me to track when people click on the plot:
               click="click"),
    plotOutput("driver"), #this plot will be created below
    br(), br(), br(), br() #line breaks to extend the page
  )
)

#Define server function
#Every server function will take the same arguments: input, output, and session
server <- function(input, output, session) {
  vals = reactiveValues(x=NULL, y=NULL) #I am going to be storing the drawings people do in this "vals" object.
  #To do so I need to create it here first. Reactive vals can change in your code, updating what appears in the shiny app
  draw = reactiveVal(FALSE) #I am creating a variable called draw and setting it as FALSE
  plot_future_obs = reactiveVal(FALSE) 
  obs_now = reactiveValues(datetime = obs$datetime, O2_mgL = obs$O2_mgL) #creating a reactiveVals object to store observations
  
  observe({
    #observe if someone changes the year. If so, reset to the first day of that year
    updateSliderInput(session, "date", value = min(start[year(start)==input$year])+15, min = min(start[year(start)==input$year])+15, 
                      max = max(stop[year(stop)==input$year]))
  })
  
  observeEvent(input$date,{ #Observe if someone changes the forecast date
    plot_future_obs(F) #Set plot_future_obs to FALSE. THis means that points past the forecast date will not be shown
    vals$x <- NULL #Clear x and y values from the human-made forecast
    vals$y <- NULL
    new_obs <- obs%>% #Select observations from this year before the forecast date
      filter(datetime <= input$date,
             datetime >= start[year(start)==input$year])
    obs_now$datetime = new_obs$datetime; obs_now$O2_mgL = new_obs$O2_mgL #enter these new values into the current observations dataframe
  })
  
  
  submitModal <- function() { #This creates the dialog box that pops up when you finish drawing your forecast
    modalDialog(
      span('Great forecast! Is that your final answer?'), 
      
      footer = tagList(
        actionButton("reset2", "reset"), #these buttons will be defined later in the code
        actionButton("submit", "submit")
      )
    )
  }
  
  observeEvent(input$click, handlerExpr = { #Observe if someone clicks on the graph
    if(draw()) { #If the person is currently drawing
      draw(F) #Stop drawing (set the variable "draw" to FALSE, this will be used later in the code)
      vals$x <- c(vals$x, NA)
      vals$y <- c(vals$y, NA)
    }
    if(!draw()){ #If they are not already drawing
      if(input$click$x > max(obs_now$datetime)-2 & input$click$x < max(obs_now$datetime)+2){ #If they clicked in the right place
        draw(T) #Start drawing
        #No matter where exactly they clicked, start the line from where they were supposed to click:
        vals$x <- c(vals$x, max(obs_now$datetime)) 
        vals$y <- c(vals$y, obs_now$O2_mgL[which.max(obs_now$datetime)])
        #The rest of the line will be created by hovering (function below)
      }
    }
  })
  
  observeEvent(input$hover, {#Observe if the person is hovering their cursor over the graph
    if (draw()) {#If "draw" is set to TRUE (they are currently drawing)
      #If they are hovering in a valid location
      if(input$hover$x <= input$date+14 & input$hover$x >= max(obs_now$datetime) & input$hover$x <= max(stop[year(stop)==input$year])){
        if(input$hover$x>vals$x[length(vals$x)]){#This prevents the line from doubling back
          vals$x <- c(vals$x, input$hover$x)# Add their current location to the list of values for their drawing
          vals$y <- c(vals$y, input$hover$y)
        }
      }
      #If they go beyond the end of the forecast period, submit the forecast
      if(input$hover$x >= input$date+14 | input$hover$x >= max(stop[year(stop)==input$year])){
        vals$x <- c(vals$x, input$date+14)# The final x value is the last day of the forecasting period
        vals$y <- c(vals$y, input$hover$y)
        draw(F) #Stop drawing
        showModal(submitModal()) #Show the submit forecast modal
      }
  }})
  
  observeEvent(input$reset, handlerExpr = { #If someone presses reset, clear their drawing and do not plot future observations
    vals$x <- NULL; vals$y <- NULL
    plot_future_obs(F)
  })
  
  observeEvent(input$reset2, handlerExpr = {
    vals$x <- NULL; vals$y <- NULL #If someone presses reset from the submit forecast modal, do the same thing
    removeModal()
  })
  
  #This long function takes peoples submitted forecasts, saves them in a spreadsheet, 
  #plots future observations, and shows them how well they did
  observeEvent(input$submit, handlerExpr = { 
    results <- read_csv("human_forecasts.csv") #load previous forecasts
    x_raw <- as.Date(vals$x[!is.na(vals$x)], origin = "1970-01-01") #convert the x values from hovering into dates
    y_raw <- vals$y[!is.na(vals$x)] #Same for y vals
    #The goal with the next couple of lines of code is to get oxygen predictions at each date.
    #First, get the desired dates:
    x <- seq(as.Date(input$date, origin = "1970-01-01"),(as.Date(input$date, origin = "1970-01-01")+14),by = 1)
    y <- approx(x_raw,y_raw,x)$y #Now approximate values at those points
    time_created <- Sys.time() #Get the time the forecast was made to add to the saved data
    initials <- "TEST" #Save who did the forecast. Right now this is always set to TEST
    TODAY <- as.Date(input$date, origin = "1970-01-01") #Get the date of the forecast 
    to_submit <- data.frame(TODAY,x,y,initials,time_created) #put these together in a dataframe
    results = results %>% #add to the forecasts that had already been made
      full_join(to_submit)
    write_csv(results,"human_forecasts.csv") #upload
    
    #Next, we need to get observations to compare to the forecasts people made. 
    obs_future <- obs%>% # Filter to only include future observations
      filter(datetime >= as.Date(input$date, origin = "1970-01-01"),
             datetime <= as.Date(input$date, origin = "1970-01-01")+14)%>%
      left_join(to_submit,by = c("datetime" = "x")) #Add peoples observations
        
    output$score_block = renderUI({tagList( #Create a score board that shows RMSE
      hr(), #horizontal line
      h3("Your guess was off by an average of:"), #text
      h1(paste(round(rmse(obs_future$O2_mgL, obs_future$y),2),"mg/L")) #score
    )})
    
    removeModal() 
    plot_future_obs(T) #DO plot future observations!
  })
  
  
  #Now, lets put together the plot itself
  output$plot= renderPlot({
    
    plot(x=obs_now$datetime, y=obs_now$O2_mgL, #plot oxygen over time
         type="p", pch = 19, cex = 1, #format points
         ylab="Oxygen concentration (mg/L)", 
         xlab="", 
         xlim = c(start[year(start)==input$year], #plot from the start of the year to 15 days past the day of the forecast
                  min(as.Date(input$date, origin = "1970-01-01")+15,
                      max(stop[year(stop)==input$year]))), #Unless the end of the forecast interval is past the end of the summer
         ylim = c(0,20))
    
    #Add a grey rectangle to indicate the forecast period
    rect(xleft = max(obs_now$datetime), #From the last observation
         xright = min(input$date+14, max(stop[year(stop)==input$year])), #To the end of the forecast period
         ybot = -5, #Extend past the top and bottom of the plot
         ytop = 25, 
         col = "lightgray", alpha = .5, border = NA)
    
    #If they have selected to also show the model, pllot that on top
    if(input$model){
      #Format the date as it is used in the filename for the archived forecast
      date = format(as.Date(input$date, origin = "1970-01-01"),"%d%b%y") 
      #Read in an archived forecast to display:
      archived <- read.csv(paste("../Archived_forecasts/29Apr20/",input$year,"/",date,".csv",sep = "")) 
      #Calculate the mean of forecast ensembles
      mean_o2_est = apply(archived[,-1], 1, FUN = mean) 
      #Add dates to the archived forecast
      archived$dates <- seq(start[year(start)==input$year], 
                            min(as.Date(input$date, origin = "1970-01-01")+14,max(stop[year(stop)==input$year])),by = 1)
      #Plot each ensemble member
      for(i in 2:101){
        lines(archived[,i] ~ archived$dates, 
              col = 'slateblue1')
      }
      #Plot the mean
      lines(mean_o2_est ~ archived$dates, col = 'black', lwd =2)
    }
    #Add points for past observations
    points(x=obs_now$datetime, y=obs_now$O2_mgL, pch = 19, cex = 1)
    #Add a distinct point for the most recent observation
    points(x=max(obs_now$datetime), y=obs_now$O2_mgL[which.max(obs_now$datetime)],pch = 19, col = "red", cex = 2)
    #Add a vertical line for the date
    abline(v=input$date, lwd = 3)
    #Add a line with the human-made forecast
    lines(x=vals$x, y=vals$y, lwd=2)
    #Write TODAY to indicate what the vertical line means
    mtext(text = "TODAY",at = c(input$date,18))
    #If plot_future_obs is true, do so
    if(plot_future_obs()){
      obs_future <- obs%>% #Filter observations to get only future observations
        filter(datetime >= input$date,
               datetime <= input$date+14)
      points(x=obs_future$datetime, y=obs_future$O2_mgL, pch = 19, cex = 1, col = "blue") #Plot them in blue
    }
  })
  
  #Plot driver data to use in creating human-made forecasts
  output$driver = renderPlot({
    par(mfrow = c(2,1), mar = c(0.3, 4.1, 3.7, 2.1), oma = c(0,0,0,0)) #Set margins to make it look nice
    sss_now = SSS%>% #Filter the oxygenation dataframe to the correct dates
      filter(time <= input$date + 14,
             time >= start[year(start)==input$year])
    plot(start[1],-10, #Create a blank plot with the correct margins and axis text
         xlim = c(start[year(start)==input$year], min(as.Date(input$date, origin = "1970-01-01")+15,max(stop[year(stop)==input$year]))),
         ylim = c(0,0.7), 
         xlab = "",xaxt = "n", ylab = "Oxygenation (scfm)")
    #Draw a rectangle for the forecast period (as above)
    rect(xleft = max(obs_now$datetime), xright = min(input$date+14, max(stop[year(stop)==input$year])), ybot = -1, ytop = 1, col = "lightgray", alpha = .5, border = NA)
    #Plot oxygen over time
    lines(x = sss_now$time, y = sss_now$scfm, lwd = 2, col = "blue")
    #Add a line for "TODAY"
    abline(v=input$date, lwd = 3)
    #Label the plot
    mtext("Drivers", line = 1.5, cex = 2)
    
    #Now plot temperature
    par(mar = c(4, 4.1, 0, 2.1)) #set margins
    temp_now = temp%>% #filter to the correct days
      filter(datetime <= input$date,
             datetime >= start[year(start)==input$year])
    #Create a blank plot
    plot(start[1],-10, xlim = c(start[year(start)==input$year], min(as.Date(input$date, origin = "1970-01-01")+15,max(stop[year(stop)==input$year]))), ylim = c(0,20), ylab = "Temp. (ºC)", xlab = "")
    #Add data
    lines(x = temp_now$datetime, y = temp_now$Temp, lwd = 2, col = "red")
    #Add a rectangle
    rect(xleft = max(obs_now$datetime), xright = (input$date+14), ybot = -5, ytop = 25, col = "lightgray", alpha = .5, border = NA)
    #Add a vertical line
    abline(v=input$date, lwd = 3)
  })
  
  #If the forecast has been submitted, plot_future_obs() will be marked TRUE. In that case, add a next forecast button to the side panel
  output$next_forecast <-renderUI(expr = if (plot_future_obs()) {
    actionButton("next_forecast","next")
    } else {NULL})
  
  #If someone clicks the next forecast button, advance the forecast date by 2 weeks
  observeEvent(input$next_forecast, handlerExpr = {
    updateSliderInput(session, "date", value = input$date+14, min = min(start[year(start)==input$year])+15, 
                      max = max(stop[year(stop)==input$year]))
  })
}

# Create Shiny object
shinyApp(ui = ui, server = server)
```

