---
title: "Shiny"
author: "Abby Lewis"
date: "4/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Load packages
library(shiny)
library(shinythemes)
library(tidyverse)
library(readr)
library(lubridate)
library(readxl)
library(Metrics)
```


A shiny app to get expert predictions as a null model

TO DO
- Deal with the connection between lines/put back people's previous guesses
- Paired test comparing people to the model at each point
- Add grey dotted lines for oxygenation changes
- Don't show the whole season (but do show the past)
- Why the flash of data when you switch years
- Mixed manager-model option (archive full model and display)
- Have people input full name to start
- Set up intervals that it progressively moves through


DONE
- Set up a plot to take predictions. Only include observation (no model) 
- Get shiny to record point clicks
- Add a button to reset
- Plot oxygenation in a figure below
- People need to click on today to make their prediction (within some interval). If not exact, adjust to exact
- Add a button to submit forecast (bonus if this is a popup)
- When people submit forecasts, the future observations show up
- Automatically stop when they reach 14 days
- Get fancy with what is allowed: don't allow cursor to double back
- Set up a database to store point clicks/hover
- Set up a widget to show people's RMSE



#```{r}
x<-as.Date("2019-08-01")
y<-10
initials <- "TEST"
TODAY <- as.Date("2019-08-01")
time_created <- Sys.time()
human_model <- data.frame(TODAY,x,y,initials,time_created)

write_csv(human_model,"human_forecasts.csv")
#```



```{r, include=FALSE}
start_stop <- read.csv("start_stop.csv")
start = as.Date(start_stop$start_all)
stop = as.Date(start_stop$stop_all)
year<-2019

CTD <- read.csv("../DO_modeling_data/vol_weighted_do_fcr.csv")
obs = CTD%>%
  filter(hypoVolume>0,
         !is.na(Conc))%>%
  mutate(Date = as.Date(Date)) %>%
  select(Date, Conc)%>%
  rename(datetime = Date)%>%
  group_by(datetime)%>%
  summarize(O2_mgL = mean(Conc))

SSS <- read_excel("../DO_modeling_data/Calc_HOX_flow_DO_20190320.xlsx") 
SSS$time <- as.Date(SSS$time)

temp = CTD %>%
  filter(hypoVolume>0,
         !is.na(Conc))%>%
  mutate(Date = as.Date(Date)) %>%
  select(Date, Temp)%>%
  rename(datetime = Date)%>%
  group_by(datetime)%>%
  summarize(Temp = mean(Temp))

# Define UI
ui <- fluidPage(theme = shinytheme("lumen"),
  titlePanel(h1("DO forecast",align = "center")),
  sidebarPanel(
    selectInput(inputId = "year", label = strong("Forecast Year"),
                choices = c("2019","2018","2016","2015","2014","2013"),
                selected = "2019"),
    
    sliderInput("date", strong("Forecast date"), value = min(start[year(start)==year])+14,
              min = min(start[year(start)==year])+14, max = max(stop[year(stop)==year]), step = 1),
    checkboxInput("model"),
    actionButton("reset", "reset"),uiOutput("next_forecast"),
    uiOutput("score_block")
  ),

    # Output: 
mainPanel(
    plotOutput("plot", hover=hoverOpts(id = "hover", delayType = "throttle", clip = TRUE, nullOutside = TRUE),
               click="click"),
    plotOutput("driver"), br(), br(), br(), br()
  )
)

#Define server function
server <- function(input, output, session) {
  
  vals = reactiveValues(x=NULL, y=NULL)
  draw = reactiveVal(FALSE)
  plot_future_obs = reactiveVal(FALSE)
  obs_now = reactiveValues(datetime = obs$datetime, O2_mgL = obs$O2_mgL)
  
  observe({
    #updateSelectInput(session = session, inputId = "year", label = strong("Forecast Year"),
     #                 choices = c("2019","2018","2016","2015","2014","2013"), selected = input$year)
    updateSliderInput(session, "date", value = min(start[year(start)==input$year])+15, min = min(start[year(start)==input$year])+15, 
                      max = max(stop[year(stop)==input$year]))
  })
  
  observeEvent(input$date,{
    plot_future_obs(F)
    vals$x <- NULL
    vals$y <- NULL
    new_obs <- obs%>%
      filter(datetime <= input$date,
             datetime >= start[year(start)==input$year])
    obs_now$datetime = new_obs$datetime; obs_now$O2_mgL = new_obs$O2_mgL
  })
  
  
  submitModal <- function() {
    modalDialog(
      span('Great forecast! Is that your final answer?'),
      
      footer = tagList(
        actionButton("reset2", "reset"),
        actionButton("submit", "submit")
      )
    )
  }
  
  observeEvent(input$click, handlerExpr = {
    if(draw()) {
      draw(F)
      vals$x <- c(vals$x, NA)
      vals$y <- c(vals$y, NA)
    }
    if(!draw()){
      if(input$click$x > max(obs_now$datetime)-2 & input$click$x < max(obs_now$datetime)+2){
        draw(T)
        vals$x <- c(vals$x, max(obs_now$datetime))
        vals$y <- c(vals$y, obs_now$O2_mgL[which.max(obs_now$datetime)])
      }
    }
  })
  
  observeEvent(input$hover, {
    if (draw()) {
      if(input$hover$x <= input$date+14 & input$hover$x >= max(obs_now$datetime) & input$hover$x <= max(stop[year(stop)==input$year])){
        if(input$hover$x>vals$x[length(vals$x)]){
          vals$x <- c(vals$x, input$hover$x)
          vals$y <- c(vals$y, input$hover$y)
        }
      }
      if(input$hover$x >= input$date+14 | input$hover$x >= max(stop[year(stop)==input$year])){
        vals$x <- c(vals$x, input$date+14)
        vals$y <- c(vals$y, input$hover$y)
        draw(F)
        showModal(submitModal())
      }
  }})
  
  observeEvent(input$reset, handlerExpr = {
    vals$x <- NULL; vals$y <- NULL
    plot_future_obs(F)
  })
  
  observeEvent(input$reset2, handlerExpr = {
    vals$x <- NULL; vals$y <- NULL
    removeModal()
  })
  
  observeEvent(input$submit, handlerExpr = {
    results <- read_csv("human_forecasts.csv")
    x_raw <- as.Date(vals$x[!is.na(vals$x)], origin = "1970-01-01")
    y_raw <- vals$y[!is.na(vals$x)]
    x <- seq(as.Date(input$date, origin = "1970-01-01"),(as.Date(input$date, origin = "1970-01-01")+14),by = 1)
    y <- approx(x_raw,y_raw,x)$y
    time_created <- Sys.time()
    initials <- "TEST"
    TODAY <- as.Date(input$date, origin = "1970-01-01")
    to_submit <- data.frame(TODAY,x,y,initials,time_created)
    results = results %>%
      full_join(to_submit)
    write_csv(results,"human_forecasts.csv")
    
    obs_future <- obs%>%
      filter(datetime >= as.Date(input$date, origin = "1970-01-01"),
             datetime <= as.Date(input$date, origin = "1970-01-01")+14)%>%
      left_join(to_submit,by = c("datetime" = "x"))
        
    output$score_block = renderUI({tagList(
      hr(),
      h3("Your guess was off by an average of:"),
      h1(paste(round(rmse(obs_future$O2_mgL, obs_future$y),2),"mg/L"))
    )})
    
    removeModal()
    plot_future_obs(T)
  })
  
  output$plot= renderPlot({
    plot(x=obs_now$datetime, y=obs_now$O2_mgL, pch = 19, cex = 1, ylab="Oxygen concentration (mg/L)", xlab="", type="p", xlim = c(min(start[year(start)==input$year]), min(as.Date(input$date, origin = "1970-01-01")+15,max(stop[year(stop)==input$year]))), ylim = c(0,20))
    rect(xleft = max(obs_now$datetime), xright = min(input$date+14, max(stop[year(stop)==input$year])), ybot = -5, ytop = 25, col = "lightgrey", alpha = .5, border = NA)
#    if(input$model){
#      date = format(as.Date(input$date, origin = "1970-01-01"),"%d%b%y")
#      archived <- read.csv(paste("../Archived_forecasts/23Mar20/",input$year,"/",date,".csv",sep = ""))
#      mean_o2_est = apply(archived[-1,], 1, FUN = mean) #make sure this is really omitting the first column
#      archived$dates <- seq(min(start[year(start)==input$year]), min(as.Date(input$date, origin = "1970-01-01")+15,max(stop[year(stop)==input$year])))
#      lines(mean_o2_est ~ archived$dates, col = 'black', lwd =2 )
#      for(i in 2:101){
#        lines(archived[,i] ~ archived$dates, 
#              col = 'grey')
#      }
#    }
    points(x=obs_now$datetime, y=obs_now$O2_mgL, pch = 19, cex = 1)
    points(x=max(obs_now$datetime), y=obs_now$O2_mgL[which.max(obs_now$datetime)],pch = 19, col = "red", cex = 2)
    abline(v=input$date, lwd = 3)
    lines(x=vals$x, y=vals$y, lwd=2)
    mtext(text = "TODAY",at = c(input$date,18))
    if(plot_future_obs()){
      obs_future <- obs%>%
        filter(datetime >= input$date,
               datetime <= input$date+14)
      points(x=obs_future$datetime, y=obs_future$O2_mgL, pch = 19, cex = 1, col = "blue")
    }
  })
  
  output$driver = renderPlot({
    par(mfrow = c(2,1), mar = c(0.3, 4.1, 3.7, 2.1), oma = c(0,0,0,0))
    sss_now = SSS%>%
      filter(time <= input$date + 14,
             time >= start[year(start)==input$year])
    plot(start[1],-10, xlim = c(min(start[year(start)==input$year]), min(as.Date(input$date, origin = "1970-01-01")+15,max(stop[year(stop)==input$year]))), ylim = c(0,0.7), xlab = "",xaxt = "n", ylab = "Oxygenation (scfm)")
    rect(xleft = max(obs_now$datetime), xright = min(input$date+14, max(stop[year(stop)==input$year])), ybot = -1, ytop = 1, col = "lightgrey", alpha = .5, border = NA)
    lines(x = sss_now$time, y = sss_now$scfm, lwd = 2, col = "blue")
    abline(v=input$date, lwd = 3)
    mtext("Drivers", line = 1.5, cex = 2)
    
    par(mar = c(4, 4.1, 0, 2.1))
    temp_now = temp%>%
      filter(datetime <= input$date,
             datetime >= start[year(start)==input$year])
    plot(start[1],-10, xlim = c(min(start[year(start)==input$year]), min(as.Date(input$date, origin = "1970-01-01")+15,max(stop[year(stop)==input$year]))), ylim = c(0,20), ylab = "Temp. (ºC)", xlab = "")
    lines(x = temp_now$datetime, y = temp_now$Temp, lwd = 2, col = "red")
    rect(xleft = max(obs_now$datetime), xright = (input$date+14), ybot = -5, ytop = 25, col = "lightgrey", alpha = .5, border = NA)
    abline(v=input$date, lwd = 3)
  })
  
  output$next_forecast <-renderUI(expr = if (plot_future_obs()) {
    actionButton("next_forecast","next")
    } else {NULL})
  
  observeEvent(input$next_forecast, handlerExpr = {
    input$date<-input$date+14
  })
}

# Create Shiny object
shinyApp(ui = ui, server = server)
```

