---
title: "Bayes_DO"
author: "Abby Lewis"
date: "2/3/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Copied from Mary's file but set up as .Rmd
2020-02-03: Can confirm that Mary's file runs
2020-02-04: Model is running and generally works well! Issues with 2016, 2015, and 2014. 2018 has insane uncertainty
2020-02-19: Updated with parameter values and model structure from GLM-AED. Used a log-normal distribution so that ko2 and R20 shouldn't be able to go negative. 2016 is pretty good now, but everything else is worse.
2020-04-15: Updating Bayes work to match EnKF and choose initial parameters. This is not even close to complete
```{r}
# State-space model - revised by S. LaDeau (11/2017) from the EcoForecast Activity by Michael Dietze, with reference "Ecological Forecasting", chapter 8
# ========================================================
#   
#   

#I don't think you will actually need all these packages for the truncated script
#but leaving them in for now
library(tidyverse)
library(readxl)
library(rjags)
library(runjags)
library(moments)
library(geosphere)
library(lubridate)
source('./JAGS_function_AED_ASL.R') 
```


- Things to note from model changes. Currently not including inflow, outflow, or entrainment
- No idea how to choose distributions
```{r}
#1) Model options => pick date range, site, time step, and type of model -----------------------------------------------------

model_name = 'Seasonal_DO_model_AED' # options are Seasonal_DO_model_AED and Seasonal_DO_model_Pace
#Creating my own model in this file
model=paste0("./",model_name, '.R')

#My local directory - use as a file repository for plot files 
my_directory <- "."
```

Updated with my observations and driver data
```{r}
#2) read in and visualize data ------------------------------------------------------------------------------------------------------------
#Edit working directory to be where file is stored on your computer
start_stop = read_csv("../DO_modeling_data/start_stop.csv")
year <- 2013

obs = read_csv("DO_observed_daily.csv") %>%
  mutate(datetime = as.Date(datetime))%>%
  filter(year(datetime) == year,
         datetime<=start_stop$stop_all[year(start_stop$stop_all) == year],
         datetime>=start_stop$start_all[year(start_stop$start_all) == year])
first = min(which(!is.na(obs$O2_mgL)))
start_date <- obs$datetime[first]
obs_cut <- obs[first:nrow(obs),]
y = t(obs_cut[,2])


drivers <- read_csv("driver_data.csv")%>%
  mutate(datetime = as.Date(datetime))%>%
  filter(year(datetime) == year,
         datetime<=start_stop$stop_all[year(start_stop$stop_all) == year],
         datetime>=start_stop$start_all[year(start_stop$start_all) == year])
SSS     <- t(drivers$SSS)
inflow  <- t(drivers$inflow)
outflow <- t(drivers$outflow)
entrain <- t(drivers$entrain)
temp    <- t(drivers$temp)
vol     <- t(drivers$hypo_volume)
  
#setting objects that are referred to in model
years <- year #only doing one year at a time at this point
year_no = as.numeric(as.factor(years))
season_days = seq(1:length(y))
```

```{r}
#3) JAGS Plug-Ins -----------------------------------------------------------------------------------------------------
jags_plug_ins <- jags_plug_ins(model_name = model_name)
# Now that we've defined the model, the data, and the initialization, we need to send all this info to JAGS, which will return the JAGS model object.
```

```{r}
#4) Run model (no edits, unless you want to change # of iterations) -------------------------------------------------------------
j.model   <- jags.model (file = model,
                         data = jags_plug_ins$data.model,
                         inits = jags_plug_ins$init.model,
                         n.chains = 3)

jags.out <- run.jags(model = model,
                     data = jags_plug_ins$data.model,
                     adapt =  5000, 
                     burnin =  5000, #100000
                     sample = 5000, 
                     n.chains = 3, 
                     inits=jags_plug_ins$init.model,
                     monitor = jags_plug_ins$variable.namesout.model)
```

```{r}
#5) Generate and save parameter traceplots and posterior distributions
write.jagsfile(jags.out, file=file.path("./JAGS_outputs/",paste(year,paste0(model_name,'.txt'), sep = '_')), 
               remove.tags = TRUE, write.data = TRUE, write.inits = TRUE)

params <- jags_plug_ins$params.model

for (i in 1:length(params)){
  png(file=file.path("./Traceplots/",paste(paste0(year,model_name,'_Convergence_',params[i],'.png'), sep = '_')))
  plot(jags.out, vars = params[i]) 
  dev.off()
}


#need to view this to get parameter estimates for model comparison Excel file
sum <- summary(jags.out, vars = jags_plug_ins$variable.names.model)

#save average parameter value results
sink(file = file.path("./JAGS_outputs/",paste(year,paste0(model_name,'_param_summary.txt'), sep = '_')))
print("Parameter summary")
sum
sink()
```

```{r}
#6) CI Calculations

#getting rjags output into matrix form
jags.out.mcmc <- as.mcmc.list(jags.out)
out <- as.matrix(jags.out.mcmc)

#get dates and observations again
dat <- obs_cut

times <- dat$datetime

#setting functions to calculate ci
ciEnvelope <- function(x,ylo,yhi,...){
  polygon(cbind(c(x, rev(x), x[1]), c(ylo, rev(yhi),
                                      ylo[1])), border = NA,...) 
}

#pulling out latent state from model output
mus=c(grep("mu\\[1,", colnames(out)),grep("mu\\[2,", colnames(out)),
      grep("mu\\[3,", colnames(out)),grep("mu\\[4,", colnames(out)),
      grep("mu\\[5,", colnames(out)),grep("mu\\[6,", colnames(out)))
mu = out[,mus]


#calculating ci of latent state
ci <- apply(mu,2,quantile,c(0.025,0.5,0.975))


ys = dat$O2_mgL #add in other years if you ever get to that point


```

```{r}
#7) CI, PI, Obs PI Plots


#CI, PI, Obs PI
png(file=file.path(my_directory,paste("Season_plots/",paste(year, model_name,'CI_PI.png', sep = '_'),sep = "")), res=300, width=20, height=15, units='cm')

#2019
plot(times,ci[2,],type='n', ylab="Oxygen concentration (mg/L)", ylim = c(min(ci[1,], na.rm = TRUE),max(ci[3,], na.rm = TRUE)),
     main="",xlab = "")
ciEnvelope(times,ci[1,],ci[3,],col="lightBlue")
points(times,ys,pch="+",cex=0.8)

title(main=paste(year,"Obs (+), Latent CI (blue)")) 


dev.off()
```
